\section{Conclusion and Future Work}
\label{sec:conclusion}

\subsection{Challenges and Limitations}

\subsubsection{Evaluation Environment Limitations}

Within an individual evaluation run, the node processes were generally executed on the same physical machine.
Therefore, the experiments represent a multi-process simulation of a distributed deployment rather than a controlled
deployment in which each node runs on a separate computer. This design enables repeatable automated testing but may
introduce resource contention among the Java processes, including CPU scheduling delays, memory pressure,
garbage-collection pauses, and delayed network-message processing.

\subsubsection{Failure-Detection Limitations}

No artificial packet loss, transmission delay, bandwidth limitation, or network partition was introduced during the
automated evaluation. Thus, the effectiveness of the SWIMPHI hybrid protocol was not tested unlike the other protocols.

\subsubsection{Concurrent Node Joining}
\label{subsubsec:concurrent-node-joining}

During FINDING NEMO protocol, there is a large proportion of runs that ended up with a few deficient nodes (nodes that
have less than the required maximum neighbors count), and the network fails to converges during the timeout (but even
if the network was allowed to continued running, the network will stay like that). However, we have previously stated
that this behaviour is expected.

When multiple nodes join the network at almost the same time, all of these nodes send a broadcast message each to the
network. The replied are collected and each new node will create its own join plan individually. These join plans may
have duplicate target nodes, for simplicity we will denoted as node $A$. This node $A$ will then receive requests from
multiple new joining nodes. Let's assume that node $A$ is deficient before this, but can only accept 1 extra new
neighbor. When node $A$ receives several requests, only the first one will be accepted, the rest will be denied.

This scenario can happen many times during a large joining session like this. One case that can happen is for a new
node to have several denied request, while all other requests from other joining nodes are accepted. Thus, after all
requests were completed, only one node remains deficient. This node does not have any other deficient nodes to start
the CHUALANH protocol with and will remain deficient until a new node joins or a node becomes deficient. This problem
can be easily detected internally by each nodes. The proposed solution will be discussed in
Section~\ref{subsubsec:node-self-recovery}. Another case that can lead to this problem is for the two deficient nodes
to have the same neighbor list. The CHUALANH protocol does not prevent this case to recovery, but the exact
implementation will be costly for finding an edge without each node to know the full topology of the network.
Therefore, our implementation only allows the selected edge to be from the neighbor list of the deficient nodes. The
proposed solution is to either implement the exact procedure - which will be very costly - or implement the solution in
Section~\ref{subsubsec:node-self-recovery}.

\subsubsection{Multiple Concurrent Node Termination}
\label{subsubsec:multiple-node-termination}

Another major problem that was revealed during testing was when too many nodes terminated at roughly the same time.
This causes the majority of nodes to become deficient with multiple missing neighbors. This proves to be a substantial
challenge for the network to converge. A large burst of recovery messages sending at the same time congests the
network, causing delay with unprocessed requests, invalid requests... To address this problem, we suggest evaluating on
a larger scale system, with multiple machines communicating in a LAN, as stated in
Section~\ref{subsubsec:large-scale-evaluation}.

\subsubsection{Presented Code}

The presented code in this document is simplified and taken from a certain snapshot. The current implementation might
be changed slightly, but the core idea remains the same.

\subsection{Future Work}

\subsubsection{Node Self-Recovery}
\label{subsubsec:node-self-recovery}
To address the problem of the network being impossible to converges, we proposed this solution. Each node will have an
internal timeout. The timeout will start or restart right after the neighbor list of that node changes and will be
active while the node is still deficient. When the timeout ends, the node will remove itself from the network and
restart after a short time. The recovery phase R in the Five-Phase Evaluation Plan is intended to simulate this
behaviour. Future improvement for this project would be to implement this behaviour for each node.

\subsubsection{Multi-Machine and Large-Scale Evaluation}
\label{subsubsec:large-scale-evaluation}

Due to hardware limitations, most experiments were conducted by running all node processes on a single laptop. This may
introduce resource contention and delay message processing, especially when many nodes recover simultaneously. Future
work should repeat the evaluation on multiple machines connected through a LAN. Comparing the results would help
determine whether the observed failures are mainly caused by single-machine resource limitations or by weaknesses in
the protocol and its implementation.

\subsection{Conclusion}

This work presented a decentralized node health-monitoring framework that integrates FINDING NEMO for neighbor
discovery, hybrid SWIMPHI for failure detection, and CHUALANH for topology recovery. The evaluation shows that the
framework performs reliably during initial network formation, node addition, and recovery from isolated node failures.
However, its performance decreases under multiple simultaneous failures due to concurrent recovery operations and
limited local topology knowledge. Overall, the results demonstrate the feasibility of the proposed approach while
highlighting the need for improved recovery coordination and larger-scale multi-machine evaluation.
