---
title: "Evaluation Statistics"
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex: false
geometry: margin=1in
fontsize: 11pt
header-includes:
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 7,
  fig.height = 4.5,
  fig.pos = "H",
  dev = "pdf",
  fig.path = "figures/"
)

library(tidyverse)
library(lubridate)
library(scales)
library(knitr)

theme_set(theme_minimal(base_size = 11))
options(knitr.kable.NA = "")
```

```{r data}
candidate_files <- c(
  "results.csv"
)

data_file <- candidate_files[file.exists(candidate_files)][1]

if (is.na(data_file)) {
  stop("Place evaluation_results.csv in the same directory as this Rmd file.")
}

results <- read_csv(
  data_file,
  show_col_types = FALSE,
  progress = FALSE
) %>%
  mutate(
    row_id = row_number(),
    run_id = cumsum(phase == "Phase 1"),
    timestamp = ymd_hms(timestamp, quiet = TRUE),
    elapsed_seconds = elapsed_ms / 1000,
    status = factor(status, levels = c("PASS", "TIMEOUT", "FAIL"))
  )

main_phases <- c(
  "Phase 1", "Phase 2.1", "Phase 2.2",
  "Phase 3", "Phase 4", "Phase 5"
)

recovery_map <- tribble(
  ~primary_phase, ~recovery_phase,
  "Phase 1",       "R1",
  "Phase 3",       "R3",
  "Phase 4",       "R4",
  "Phase 5",       "R5"
)

stability_phases <- c("S1", "S3", "S4", "S5", "SR")
status_levels <- c("PASS", "TIMEOUT", "FAIL")
```

```{r helpers}
empty_plot <- function(label) {
  ggplot() +
    annotate("text", x = 0, y = 0, label = label, size = 4) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    theme_void()
}

status_data <- function(phases) {
  counts <- results %>%
    filter(phase %in% phases) %>%
    count(phase, status, name = "n") %>%
    mutate(status = as.character(status))

  expand_grid(
    phase = phases,
    status = status_levels
  ) %>%
    left_join(counts, by = c("phase", "status")) %>%
    mutate(n = replace_na(n, 0L)) %>%
    group_by(phase) %>%
    mutate(
      total = sum(n),
      share = if_else(total > 0, n / total, 0),
      label = if_else(
        n > 0,
        paste0(status, "\n", n, " (", percent(share, accuracy = 0.1), ")"),
        ""
      )
    ) %>%
    ungroup() %>%
    mutate(
      phase = factor(phase, levels = phases),
      status = factor(status, levels = status_levels)
    )
}

plot_success_pies <- function(phases, title = "Success rate") {
  d <- status_data(phases) %>% filter(n > 0)

  ggplot(d, aes(x = "", y = n, fill = status)) +
    geom_col(width = 1) +
    geom_text(
      aes(label = label),
      position = position_stack(vjust = 0.5),
      size = 3.2
    ) +
    coord_polar(theta = "y") +
    facet_wrap(~ phase) +
    labs(title = title, fill = "Status") +
    theme_void() +
    theme(
      plot.title = element_text(hjust = 0.5),
      strip.text = element_text(face = "bold")
    )
}

plot_completion <- function(phases, title = "Completion time") {
  d <- results %>%
    filter(phase %in% phases) %>%
    mutate(phase = factor(phase, levels = phases))

  passed <- d %>% filter(status == "PASS")

  if (nrow(d) == 0) {
    return(empty_plot("No observations"))
  }

  ggplot() +
    geom_boxplot(
      data = passed,
      aes(x = phase, y = elapsed_seconds),
      width = 0.55,
      outlier.shape = NA
    ) +
    geom_jitter(
      data = d,
      aes(x = phase, y = elapsed_seconds, shape = status),
      width = 0.12,
      height = 0,
      size = 2,
      alpha = 0.75
    ) +
    labs(
      title = title,
      x = NULL,
      y = "Elapsed time (seconds)",
      shape = "Status"
    ) +
    theme(
      plot.title = element_text(hjust = 0.5),
      legend.position = "bottom"
    )
}

timing_summary <- function(phases) {
  results %>%
    filter(phase %in% phases, status == "PASS") %>%
    mutate(phase = factor(phase, levels = phases)) %>%
    group_by(phase) %>%
    summarise(
      n = n(),
      mean_s = mean(elapsed_seconds),
      median_s = median(elapsed_seconds),
      sd_s = sd(elapsed_seconds),
      p90_s = quantile(elapsed_seconds, 0.90),
      min_s = min(elapsed_seconds),
      max_s = max(elapsed_seconds),
      .groups = "drop"
    )
}

plot_failed_problem_counts <- function(phases, title = "Problem count in failed runs") {
  d <- results %>%
    filter(phase %in% phases, status != "PASS") %>%
    count(phase, problem_count, name = "runs") %>%
    mutate(phase = factor(phase, levels = phases))

  if (nrow(d) == 0) {
    return(empty_plot("No failed observations"))
  }

  ggplot(d, aes(x = factor(problem_count), y = runs)) +
    geom_col() +
    facet_wrap(~ phase, scales = "free_y") +
    scale_y_continuous(breaks = pretty_breaks()) +
    labs(
      title = title,
      x = "Deficient/problematic nodes",
      y = "Failed runs"
    ) +
    theme(plot.title = element_text(hjust = 0.5))
}

recovery_attempt_data <- function(primary_phase, recovery_phase) {
  primary_failures <- results %>%
    filter(phase == primary_phase, status != "PASS") %>%
    select(
      run_id,
      primary_status = status,
      primary_problem_count = problem_count
    )

  recovery_rows <- results %>%
    filter(phase == recovery_phase) %>%
    select(
      run_id,
      recovery_status = status,
      recovery_elapsed_seconds = elapsed_seconds,
      recovery_problem_count = problem_count
    )

  primary_failures %>%
    left_join(recovery_rows, by = "run_id")
}

recovery_summary <- function(primary_phase, recovery_phase) {
  primary_rows <- results %>% filter(phase == primary_phase)
  d <- recovery_attempt_data(primary_phase, recovery_phase)

  failed <- nrow(d)
  attempted <- sum(!is.na(d$recovery_status))
  passed <- sum(d$recovery_status == "PASS", na.rm = TRUE)
  primary_passed <- sum(primary_rows$status == "PASS")

  tibble(
    phase = primary_phase,
    recovery = recovery_phase,
    primary_runs = nrow(primary_rows),
    primary_passes = primary_passed,
    primary_failures = failed,
    recovery_attempts = attempted,
    recovery_passes = passed,
    recovery_success_pct = if_else(
      attempted > 0,
      100 * passed / attempted,
      NA_real_
    ),
    final_success_pct = if_else(
      nrow(primary_rows) > 0,
      100 * (primary_passed + passed) / nrow(primary_rows),
      NA_real_
    )
  )
}

plot_recovery <- function(primary_phase, recovery_phase) {
  d <- recovery_attempt_data(primary_phase, recovery_phase) %>%
    filter(!is.na(recovery_status)) %>%
    count(recovery_status, name = "n") %>%
    mutate(
      share = n / sum(n),
      label = paste0(
        recovery_status, "\n",
        n, " (", percent(share, accuracy = 0.1), ")"
      )
    )

  if (nrow(d) == 0) {
    return(empty_plot("Recovery was not executed"))
  }

  ggplot(d, aes(x = "", y = n, fill = recovery_status)) +
    geom_col(width = 1) +
    geom_text(
      aes(label = label),
      position = position_stack(vjust = 0.5),
      size = 3.2
    ) +
    coord_polar(theta = "y") +
    labs(
      title = paste(recovery_phase, "success"),
      fill = "Status"
    ) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5))
}

all_recovery_summary <- pmap_dfr(
  recovery_map,
  recovery_summary
)

final_outcomes <- map2_dfr(
  recovery_map$primary_phase,
  recovery_map$recovery_phase,
  function(primary_phase, recovery_phase) {
    primary <- results %>%
      filter(phase == primary_phase) %>%
      select(run_id, primary_status = status)

    recovery <- results %>%
      filter(phase == recovery_phase) %>%
      select(run_id, recovery_status = status)

    primary %>%
      left_join(recovery, by = "run_id") %>%
      mutate(
        outcome = case_when(
          primary_status == "PASS" ~ "Primary pass",
          recovery_status == "PASS" ~ "Recovered",
          TRUE ~ "Unrecovered"
        ),
        phase = primary_phase
      ) %>%
      count(phase, outcome, name = "runs")
  }
)
```

# Dataset

```{r dataset-summary}
dataset_summary <- tibble(
  statistic = c(
    "Rows",
    "Runs started",
    "Runs reaching Phase 5",
    "PASS records",
    "TIMEOUT records",
    "FAIL records"
  ),
  value = c(
    nrow(results),
    n_distinct(results$run_id),
    n_distinct(results$run_id[results$phase == "Phase 5"]),
    sum(results$status == "PASS"),
    sum(results$status == "TIMEOUT"),
    sum(results$status == "FAIL")
  )
)

kable(dataset_summary, align = c("l", "r"))
```

```{r main-phase-summary}
main_phase_summary <- results %>%
  filter(phase %in% main_phases) %>%
  group_by(phase) %>%
  summarise(
    n = n(),
    passes = sum(status == "PASS"),
    timeouts = sum(status == "TIMEOUT"),
    failures = sum(status == "FAIL"),
    success_pct = 100 * mean(status == "PASS"),
    .groups = "drop"
  ) %>%
  mutate(phase = factor(phase, levels = main_phases)) %>%
  arrange(phase)

kable(main_phase_summary, digits = 2, align = c("l", rep("r", 5)))
```

# Phase 1

## Success rate

```{r phase1-success, fig.height=4.5}
plot_success_pies("Phase 1")
```

## Completion time

```{r phase1-time, fig.height=4.5}
plot_completion(c("Phase 1", "R1"))
```

```{r phase1-time-table}
kable(
  timing_summary(c("Phase 1", "R1")),
  digits = 2,
  align = c("l", rep("r", 7))
)
```

## Failed runs

```{r phase1-problems}
plot_failed_problem_counts("Phase 1")
```

## Recovery

```{r phase1-recovery, fig.height=4}
plot_recovery("Phase 1", "R1")
```

```{r phase1-recovery-table}
kable(
  recovery_summary("Phase 1", "R1"),
  digits = 2,
  align = c("l", "l", rep("r", 7))
)
```

# Phase 2

## Success rate

```{r phase2-success, fig.height=4.5}
plot_success_pies(c("Phase 2.1", "Phase 2.2"))
```

## Completion time

```{r phase2-time}
plot_completion(c("Phase 2.1", "Phase 2.2"))
```

```{r phase2-time-table}
kable(
  timing_summary(c("Phase 2.1", "Phase 2.2")),
  digits = 2,
  align = c("l", rep("r", 7))
)
```

## Detection propagation delay

```{r phase2-delay, fig.height=4.5}
phase2_delay <- results %>%
  filter(phase %in% c("Phase 2.1", "Phase 2.2"), status == "PASS") %>%
  select(run_id, phase, elapsed_seconds) %>%
  pivot_wider(names_from = phase, values_from = elapsed_seconds) %>%
  filter(!is.na(`Phase 2.1`), !is.na(`Phase 2.2`)) %>%
  mutate(propagation_delay_seconds = `Phase 2.2` - `Phase 2.1`)

if (nrow(phase2_delay) > 0) {
  ggplot(
    phase2_delay,
    aes(x = "", y = propagation_delay_seconds)
  ) +
    geom_boxplot(width = 0.35, outlier.shape = NA) +
    geom_jitter(width = 0.08, size = 2, alpha = 0.75) +
    labs(
      title = "Phase 2.2 minus Phase 2.1",
      x = NULL,
      y = "Delay (seconds)"
    ) +
    theme(
      plot.title = element_text(hjust = 0.5),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank()
    )
} else {
  empty_plot("No paired observations")
}
```

```{r phase2-delay-table}
if (nrow(phase2_delay) > 0) {
  delay_summary <- phase2_delay %>%
    summarise(
      n = n(),
      mean_s = mean(propagation_delay_seconds),
      median_s = median(propagation_delay_seconds),
      sd_s = sd(propagation_delay_seconds),
      p90_s = quantile(propagation_delay_seconds, 0.90),
      min_s = min(propagation_delay_seconds),
      max_s = max(propagation_delay_seconds)
    )

  kable(delay_summary, digits = 2, align = rep("r", 7))
}
```

## Failed runs

```{r phase2-problems}
plot_failed_problem_counts(c("Phase 2.1", "Phase 2.2"))
```

# Phase 3

## Success rate

```{r phase3-success}
plot_success_pies("Phase 3")
```

## Completion time

```{r phase3-time}
plot_completion(c("Phase 3", "R3"))
```

```{r phase3-time-table}
kable(
  timing_summary(c("Phase 3", "R3")),
  digits = 2,
  align = c("l", rep("r", 7))
)
```

## Failed runs

```{r phase3-problems}
plot_failed_problem_counts("Phase 3")
```

## Recovery

```{r phase3-recovery, fig.height=4}
plot_recovery("Phase 3", "R3")
```

```{r phase3-recovery-table}
kable(
  recovery_summary("Phase 3", "R3"),
  digits = 2,
  align = c("l", "l", rep("r", 7))
)
```

# Phase 4

## Success rate

```{r phase4-success}
plot_success_pies("Phase 4")
```

## Completion time

```{r phase4-time}
plot_completion(c("Phase 4", "R4"))
```

```{r phase4-time-table}
kable(
  timing_summary(c("Phase 4", "R4")),
  digits = 2,
  align = c("l", rep("r", 7))
)
```

## Failed runs

```{r phase4-problems}
plot_failed_problem_counts("Phase 4")
```

## Recovery

```{r phase4-recovery, fig.height=4}
plot_recovery("Phase 4", "R4")
```

```{r phase4-recovery-table}
kable(
  recovery_summary("Phase 4", "R4"),
  digits = 2,
  align = c("l", "l", rep("r", 7))
)
```

# Phase 5

## Success rate

```{r phase5-success}
plot_success_pies("Phase 5")
```

## Completion time

```{r phase5-time}
plot_completion(c("Phase 5", "R5"))
```

```{r phase5-time-table}
kable(
  timing_summary(c("Phase 5", "R5")),
  digits = 2,
  align = c("l", rep("r", 7))
)
```

## Failed runs

```{r phase5-problems}
plot_failed_problem_counts("Phase 5")
```

## Recovery

```{r phase5-recovery, fig.height=4}
plot_recovery("Phase 5", "R5")
```

```{r phase5-recovery-table}
kable(
  recovery_summary("Phase 5", "R5"),
  digits = 2,
  align = c("l", "l", rep("r", 7))
)
```

# Stability phases

## Overall success

```{r stability-overall, fig.height=4}
stability_overall <- results %>%
  filter(phase %in% stability_phases) %>%
  count(status, name = "n") %>%
  mutate(
    share = n / sum(n),
    label = paste0(
      status, "\n",
      n, " (", percent(share, accuracy = 0.1), ")"
    )
  )

ggplot(stability_overall, aes(x = "", y = n, fill = status)) +
  geom_col(width = 1) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    size = 3.2
  ) +
  coord_polar(theta = "y") +
  labs(title = "All stability phases", fill = "Status") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))
```

## Success by type

```{r stability-by-type}
stability_by_type <- results %>%
  filter(phase %in% stability_phases) %>%
  count(phase, status, name = "n") %>%
  mutate(phase = factor(phase, levels = stability_phases))

ggplot(
  stability_by_type,
  aes(x = phase, y = n, fill = status)
) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = percent_format()) +
  labs(
    title = "Stability success by type",
    x = NULL,
    y = "Share",
    fill = "Status"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  )
```

```{r stability-table}
stability_summary <- results %>%
  filter(phase %in% stability_phases) %>%
  group_by(phase) %>%
  summarise(
    n = n(),
    passes = sum(status == "PASS"),
    timeouts = sum(status == "TIMEOUT"),
    failures = sum(status == "FAIL"),
    success_pct = 100 * mean(status == "PASS"),
    .groups = "drop"
  ) %>%
  mutate(phase = factor(phase, levels = stability_phases)) %>%
  arrange(phase)

kable(stability_summary, digits = 2, align = c("l", rep("r", 5)))
```

# Comparisons

## Primary success rate

```{r primary-success-comparison}
primary_success <- results %>%
  filter(phase %in% main_phases) %>%
  group_by(phase) %>%
  summarise(
    runs = n(),
    success_pct = 100 * mean(status == "PASS"),
    .groups = "drop"
  ) %>%
  mutate(phase = factor(phase, levels = main_phases))

ggplot(primary_success, aes(x = phase, y = success_pct)) +
  geom_col() +
  geom_text(
    aes(label = paste0(round(success_pct, 1), "%\n(n=", runs, ")")),
    vjust = -0.3,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, 108),
    breaks = seq(0, 100, 20),
    labels = label_percent(scale = 1)
  ) +
  labs(
    title = "Primary success rate",
    x = NULL,
    y = "Success rate"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 25, hjust = 1)
  )
```

## Outcome after recovery

```{r final-outcome-comparison}
final_outcome_plot_data <- final_outcomes %>%
  group_by(phase) %>%
  mutate(share = runs / sum(runs)) %>%
  ungroup() %>%
  mutate(
    phase = factor(
      phase,
      levels = recovery_map$primary_phase
    ),
    outcome = factor(
      outcome,
      levels = c("Primary pass", "Recovered", "Unrecovered")
    )
  )

ggplot(
  final_outcome_plot_data,
  aes(x = phase, y = share, fill = outcome)
) +
  geom_col() +
  scale_y_continuous(labels = percent_format()) +
  labs(
    title = "Outcome after recovery",
    x = NULL,
    y = "Share of runs",
    fill = "Outcome"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "bottom"
  )
```

## Recovery summary

```{r recovery-summary-table}
kable(
  all_recovery_summary,
  digits = 2,
  align = c("l", "l", rep("r", 7))
)
```

```{r recovery-success-comparison}
recovery_plot_data <- all_recovery_summary %>%
  filter(recovery_attempts > 0) %>%
  mutate(
    recovery = factor(recovery, levels = recovery_map$recovery_phase)
  )

ggplot(
  recovery_plot_data,
  aes(x = recovery, y = recovery_success_pct)
) +
  geom_col() +
  geom_text(
    aes(
      label = paste0(
        round(recovery_success_pct, 1),
        "%\n(n=", recovery_attempts, ")"
      )
    ),
    vjust = -0.3,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, 108),
    breaks = seq(0, 100, 20),
    labels = label_percent(scale = 1)
  ) +
  labs(
    title = "Recovery success rate",
    x = NULL,
    y = "Success rate"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

## Successful completion times

```{r all-times-comparison, fig.height=5}
comparison_phases <- c(
  "Phase 1", "R1",
  "Phase 2.1", "Phase 2.2",
  "Phase 3", "R3",
  "Phase 4", "R4",
  "Phase 5", "R5"
)

successful_times <- results %>%
  filter(
    phase %in% comparison_phases,
    status == "PASS"
  ) %>%
  mutate(phase = factor(phase, levels = comparison_phases))

ggplot(
  successful_times,
  aes(x = phase, y = elapsed_seconds)
) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.12, size = 1.7, alpha = 0.65) +
  labs(
    title = "Successful completion times",
    x = NULL,
    y = "Elapsed time (seconds)"
  ) +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 35, hjust = 1)
  )
```
