---
title: "Node Health Checking Evaluation Report"
author: "To Huynh Phuc"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    df_print: paged
params:
  csv_file: "results-copy.csv"
---

```{r setup, include=FALSE}
required_packages <- c(
  "tidyverse",
  "jsonlite",
  "lubridate",
  "scales",
  "knitr"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_packages) > 0) {
  install.packages(
    missing_packages,
    repos = "https://cloud.r-project.org"
  )
}

invisible(lapply(required_packages, library, character.only = TRUE))

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  out.width = "95%"
)

theme_set(theme_minimal(base_size = 12))

phase_levels <- paste("Phase", 1:5)
all_phase_levels <- c(phase_levels, "Phase R")

safe_json_field <- function(json_text, field, default = NA) {
  tryCatch({
    parsed <- jsonlite::fromJSON(json_text)
    value <- parsed[[field]]
    if (is.null(value) || length(value) == 0) default else value[[1]]
  }, error = function(e) default)
}

plural_nodes <- function(n) {
  ifelse(n == 1, "node", "nodes")
}
```

# Purpose and Classification Rules

This report evaluates repeated executions of Phases 1--5 and the conditional recovery phase, Phase R.

The following rules are applied consistently:

1.  Phases 1--5 are treated as the main evaluation phases.
2.  Phase R is analysed separately because it only runs after a phase requires recovery.
3.  A row whose metadata indicates a timeout but whose `failed_nodes_count` is zero is treated as a **success** in reliability charts.
4.  Such rows are also recorded as **logging/timing anomalies**.
5.  Anomalous rows are excluded from completion-time statistics because the timeout duration does not reveal when convergence actually occurred.
6.  A non-successful row is split by its reported number of failed nodes, for example, “Partial: 1 failed node” or “Partial: 2 failed nodes.”

# Load and Prepare the Data

```{r load-data}
csv_path <- params$csv_file

if (!file.exists(csv_path)) {
  stop(
    paste0(
      "Cannot find '", csv_path, "'. ",
      "Place the CSV file in the same folder as this R Markdown file, ",
      "or change params$csv_file in the YAML header."
    )
  )
}

results_raw <- readr::read_csv(
  csv_path,
  show_col_types = FALSE,
  na = c("", "NA", "null")
)

required_columns <- c(
  "timestamp", "phase", "status", "elapsed_ms",
  "initial_nodes", "added_node_count", "max_neighbors",
  "details", "failed_nodes_count", "metadata"
)

missing_columns <- setdiff(required_columns, names(results_raw))

if (length(missing_columns) > 0) {
  stop(
    paste(
      "The CSV is missing required columns:",
      paste(missing_columns, collapse = ", ")
    )
  )
}

results <- results_raw %>%
  mutate(
    timestamp_parsed = lubridate::ymd_hms(timestamp, quiet = TRUE),
    phase = factor(phase, levels = all_phase_levels),
    status = stringr::str_to_upper(stringr::str_trim(status)),
    timed_out = purrr::map_lgl(
      metadata,
      ~ isTRUE(safe_json_field(.x, "timed_out", FALSE))
    ),
    trigger_phase = purrr::map_chr(
      metadata,
      ~ as.character(safe_json_field(.x, "trigger_phase", NA_character_))
    ),
    timeout_zero_anomaly =
      timed_out &
      failed_nodes_count == 0,
    effective_success =
      status == "PASS" |
      timeout_zero_anomaly,
    valid_timing_success =
      effective_success &
      !timeout_zero_anomaly,
    binary_outcome = if_else(
      effective_success,
      "Success",
      "Failure"
    ),
    outcome_category = case_when(
      effective_success ~ "Success",
      failed_nodes_count > 0 ~ paste0(
        "Partial: ",
        failed_nodes_count,
        " failed ",
        plural_nodes(failed_nodes_count)
      ),
      TRUE ~ paste0(status, ": 0 failed nodes reported")
    ),
    elapsed_seconds = elapsed_ms / 1000,
    configuration = paste0(
      initial_nodes,
      " initial nodes, k = ",
      max_neighbors
    )
  ) %>%
  arrange(timestamp_parsed, timestamp) %>%
  group_by(phase) %>%
  mutate(phase_run_number = row_number()) %>%
  ungroup()

main_results <- results %>%
  filter(phase %in% phase_levels)

recovery_results <- results %>%
  filter(phase == "Phase R")
```

```{r data-preview}
cat(
  "Loaded **", nrow(results), "** rows from `",
  csv_path, "`.\n\n",
  sep = ""
)

knitr::kable(
  head(results_raw, 8),
  caption = "Preview of the imported evaluation data"
)
```

# Overall Evaluation Summary

```{r overview-table}
overview <- tibble::tibble(
  Metric = c(
    "Total CSV rows",
    "Main phase executions (Phases 1-5)",
    "Phase R executions",
    "Effective main-phase successes",
    "Effective main-phase failures",
    "Timeout-with-zero-failed-node anomalies"
  ),
  Value = c(
    nrow(results),
    nrow(main_results),
    nrow(recovery_results),
    sum(main_results$effective_success),
    sum(!main_results$effective_success),
    sum(results$timeout_zero_anomaly)
  )
)

knitr::kable(
  overview,
  caption = "High-level evaluation totals"
)
```

## Number of Executions per Main Phase

```{r phase-execution-counts, fig.height=4.8}
phase_execution_counts <- main_results %>%
  count(phase, name = "executions") %>%
  tidyr::complete(
    phase = factor(phase_levels, levels = phase_levels),
    fill = list(executions = 0)
  )

knitr::kable(
  phase_execution_counts,
  caption = "Number of executions for Phases 1-5"
)

ggplot(
  phase_execution_counts,
  aes(x = phase, y = executions)
) +
  geom_col() +
  geom_text(
    aes(label = executions),
    vjust = -0.35,
    size = 4
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.10))
  ) +
  labs(
    title = "Execution Count by Main Phase",
    x = NULL,
    y = "Number of executions"
  )
```

## Effective Success Rate by Main Phase

```{r overall-success-rate, fig.height=5}
main_binary_summary <- main_results %>%
  count(phase, binary_outcome, name = "runs") %>%
  group_by(phase) %>%
  mutate(share = runs / sum(runs)) %>%
  ungroup()

ggplot(
  main_binary_summary,
  aes(x = phase, y = share, fill = binary_outcome)
) +
  geom_col(position = "fill") +
  geom_text(
    aes(label = paste0(runs, "\n", scales::percent(share, accuracy = 0.1))),
    position = position_fill(vjust = 0.5),
    size = 3.4
  ) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Effective Success and Failure Rate by Phase",
    x = NULL,
    y = "Proportion",
    fill = "Outcome"
  )
```

# Phase-by-Phase Outcomes and Successful Completion Times

Each phase receives:

- a pie chart separating successes from partial results by the number of failed nodes; and
- a completion-time distribution for successful, non-anomalous runs.

```{r phase-by-phase, results='asis', fig.width=8, fig.height=5}
for (phase_name in phase_levels) {
  cat("\n\n## ", phase_name, "\n\n", sep = "")

  phase_data <- main_results %>%
    filter(as.character(phase) == phase_name)

  outcome_data <- phase_data %>%
    count(outcome_category, name = "runs") %>%
    mutate(
      share = runs / sum(runs),
      label = paste0(
        runs,
        "\n",
        scales::percent(share, accuracy = 0.1)
      )
    )

  cat("### Outcome distribution\n\n")

  outcome_plot <- ggplot(
    outcome_data,
    aes(x = "", y = runs, fill = outcome_category)
  ) +
    geom_col(width = 1) +
    coord_polar(theta = "y") +
    geom_text(
      aes(label = label),
      position = position_stack(vjust = 0.5),
      size = 3.5
    ) +
    labs(
      title = paste(phase_name, "Outcome Distribution"),
      fill = "Outcome"
    ) +
    theme_void(base_size = 12) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(hjust = 0.5)
    )

  print(outcome_plot)

  cat("\n\n### Successful completion-time distribution\n\n")

  timing_data <- phase_data %>%
    filter(valid_timing_success)

  if (nrow(timing_data) == 0) {
    cat("No valid successful completion-time observations are available.\n\n")
  } else {
    bin_count <- max(5, min(15, ceiling(sqrt(nrow(timing_data)))))
    median_time <- median(timing_data$elapsed_seconds, na.rm = TRUE)

    timing_plot <- ggplot(
      timing_data,
      aes(x = elapsed_seconds)
    ) +
      geom_histogram(
        bins = bin_count,
        boundary = 0
      ) +
      geom_vline(
        xintercept = median_time,
        linetype = "dashed",
        linewidth = 0.8
      ) +
      annotate(
        "text",
        x = median_time,
        y = Inf,
        label = paste0(
          "Median = ",
          round(median_time, 2),
          " s"
        ),
        vjust = 1.5,
        hjust = -0.05,
        size = 3.6
      ) +
      labs(
        title = paste(phase_name, "Successful Completion Times"),
        subtitle = "Anomalous timeout-with-zero-failure rows are excluded",
        x = "Elapsed time (seconds)",
        y = "Number of runs"
      )

    print(timing_plot)
  }

  cat("\n\n### Numerical summary\n\n")

  phase_summary <- tibble::tibble(
    Executions = nrow(phase_data),
    `Effective successes` = sum(phase_data$effective_success),
    `Effective failures` = sum(!phase_data$effective_success),
    `Success rate` = scales::percent(
      mean(phase_data$effective_success),
      accuracy = 0.1
    ),
    `Valid timing observations` = nrow(timing_data),
    `Median successful time (s)` = ifelse(
      nrow(timing_data) > 0,
      round(median(timing_data$elapsed_seconds, na.rm = TRUE), 2),
      NA_real_
    )
  )

  print(
    knitr::kable(
      phase_summary,
      caption = paste(phase_name, "summary")
    )
  )

  cat("\n\n")
}
```

# Successful Completion-Time Comparison

## Summary Statistics

```{r timing-summary-table}
successful_timing_summary <- main_results %>%
  filter(valid_timing_success) %>%
  group_by(phase) %>%
  summarise(
    successful_runs = n(),
    mean_seconds = mean(elapsed_seconds, na.rm = TRUE),
    median_seconds = median(elapsed_seconds, na.rm = TRUE),
    p95_seconds = quantile(
      elapsed_seconds,
      probs = 0.95,
      na.rm = TRUE,
      names = FALSE
    ),
    minimum_seconds = min(elapsed_seconds, na.rm = TRUE),
    maximum_seconds = max(elapsed_seconds, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    across(
      c(
        mean_seconds,
        median_seconds,
        p95_seconds,
        minimum_seconds,
        maximum_seconds
      ),
      ~ round(.x, 2)
    )
  )

knitr::kable(
  successful_timing_summary,
  caption = "Successful completion-time summary by phase"
)
```

## Distribution Comparison

```{r timing-boxplot, fig.height=5.5}
ggplot(
  main_results %>% filter(valid_timing_success),
  aes(x = phase, y = elapsed_seconds)
) +
  geom_boxplot(
    outlier.shape = NA,
    alpha = 0.25
  ) +
  geom_jitter(
    aes(
      color = initial_nodes,
      size = max_neighbors
    ),
    width = 0.16,
    alpha = 0.6
  ) +
  scale_color_gradient(
    low = "skyblue",
    high = "darkblue",
    name = "Initial nodes"
  ) +
  scale_size_continuous(
    name = "Maximum neighbors",
    range = c(1.5, 4)
  ) +
  labs(
    title = "Successful Completion-Time Distribution Across Phases",
    subtitle = paste(
      "Point color represents the initial node count;",
      "point size represents the maximum neighbor count"
    ),
    x = NULL,
    y = "Elapsed time (seconds)"
  ) +
  theme(
    legend.position = "right"
  )
```

## Performance Over Repeated Runs

This plot helps reveal warm-up effects, system slowdown, unstable periods, or changes between configurations.

```{r time-trend, fig.height=7}
ggplot(
  main_results %>% filter(valid_timing_success),
  aes(
    x = phase_run_number,
    y = elapsed_seconds
  )
) +
  geom_point(alpha = 0.55, size = 1.5) +
  geom_smooth(
    method = "loess",
    se = FALSE,
    linewidth = 0.8
  ) +
  facet_wrap(
    ~ phase,
    scales = "free_y",
    ncol = 1
  ) +
  labs(
    title = "Successful Completion Time Over Repeated Executions",
    x = "Execution number within phase",
    y = "Elapsed time (seconds)"
  )
```

# Phase R Recovery Analysis

Phase R is conditional and therefore should not be interpreted as having the same workload as Phases 1--5.

## Phase R Success/Failure Pie Chart

```{r phase-r-pie, fig.height=5.5}
phase_r_binary <- recovery_results %>%
  count(binary_outcome, name = "runs") %>%
  mutate(
    share = runs / sum(runs),
    label = paste0(
      runs,
      "\n",
      scales::percent(share, accuracy = 0.1)
    )
  )

ggplot(
  phase_r_binary,
  aes(x = "", y = runs, fill = binary_outcome)
) +
  geom_col(width = 1) +
  coord_polar(theta = "y") +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    size = 4
  ) +
  labs(
    title = "Phase R Effective Success and Failure",
    subtitle = "Timeout rows with zero failed nodes are counted as successes",
    fill = "Outcome"
  ) +
  theme_void(base_size = 12) +
  theme(
    legend.position = "bottom",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

## Phase R Outcomes by Triggering Phase

```{r phase-r-trigger-summary, fig.height=5.5}
phase_r_by_trigger <- recovery_results %>%
  mutate(
    trigger_phase = replace_na(trigger_phase, "Unknown trigger")
  ) %>%
  group_by(trigger_phase) %>%
  summarise(
    executions = n(),
    successes = sum(effective_success),
    failures = sum(!effective_success),
    success_rate = mean(effective_success),
    median_valid_time_seconds = ifelse(
      sum(valid_timing_success) > 0,
      median(
        elapsed_seconds[valid_timing_success],
        na.rm = TRUE
      ),
      NA_real_
    ),
    .groups = "drop"
  ) %>%
  mutate(
    success_rate_label = scales::percent(
      success_rate,
      accuracy = 0.1
    ),
    median_valid_time_seconds = round(
      median_valid_time_seconds,
      2
    )
  )

knitr::kable(
  phase_r_by_trigger,
  caption = "Phase R effectiveness by triggering phase"
)

ggplot(
  recovery_results %>%
    mutate(trigger_phase = replace_na(trigger_phase, "Unknown trigger")),
  aes(x = trigger_phase, fill = binary_outcome)
) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Phase R Outcome by Triggering Phase",
    x = "Triggering phase",
    y = "Share of Phase R executions",
    fill = "Outcome"
  )
```

## Phase R Failure Severity

```{r phase-r-failure-severity}
phase_r_failure_severity <- recovery_results %>%
  filter(!effective_success) %>%
  count(failed_nodes_count, name = "runs") %>%
  arrange(failed_nodes_count)

if (nrow(phase_r_failure_severity) == 0) {
  cat("No effective Phase R failures were recorded.")
} else {
  knitr::kable(
    phase_r_failure_severity,
    caption = "Number of failed nodes remaining after unsuccessful Phase R executions"
  )
}
```

# Configuration-Based Reliability

The following analysis compares outcomes using `initial_nodes` and `max_neighbors`. Because the dataset may contain only some combinations, the report shows only configurations that actually occurred.

## Configuration Summary Table

```{r configuration-table}
configuration_summary <- main_results %>%
  group_by(
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    executions = n(),
    successes = sum(effective_success),
    failures = sum(!effective_success),
    success_rate = mean(effective_success),
    median_valid_time_seconds = ifelse(
      sum(valid_timing_success) > 0,
      median(
        elapsed_seconds[valid_timing_success],
        na.rm = TRUE
      ),
      NA_real_
    ),
    .groups = "drop"
  ) %>%
  mutate(
    success_rate = scales::percent(
      success_rate,
      accuracy = 0.1
    ),
    median_valid_time_seconds = round(
      median_valid_time_seconds,
      2
    )
  )

knitr::kable(
  configuration_summary,
  caption = "Reliability summary by initial node count and maximum-neighbor setting"
)
```

## Success Rate Heatmap by Phase and Configuration

```{r configuration-heatmap, fig.height=6}
configuration_phase_summary <- main_results %>%
  group_by(
    phase,
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    executions = n(),
    successes = sum(effective_success),
    success_rate = mean(effective_success),
    .groups = "drop"
  ) %>%
  mutate(
    label = paste0(
      scales::percent(success_rate, accuracy = 0.1),
      "\n",
      successes,
      "/",
      executions
    )
  )

ggplot(
  configuration_phase_summary,
  aes(
    x = factor(initial_nodes),
    y = factor(max_neighbors),
    fill = success_rate
  )
) +
  geom_tile(
    linewidth = 0.7
  ) +
  geom_text(
    aes(label = label),
    size = 3.7
  ) +
  facet_wrap(~ phase) +
  scale_fill_gradient(
    limits = c(0, 1),
    labels = scales::percent
  ) +
  labs(
    title = "Success Rate by Initial Nodes and Maximum Neighbors",
    subtitle = "Labels show success percentage and successful runs / total runs",
    x = "Initial node count",
    y = "Maximum neighbors (k)",
    fill = "Success rate"
  )
```

## Success/Failure Proportions by Configuration

```{r configuration-stacked-bars, fig.height=6}
configuration_binary <- main_results %>%
  count(
    phase,
    configuration,
    binary_outcome,
    name = "runs"
  ) %>%
  group_by(phase, configuration) %>%
  mutate(share = runs / sum(runs)) %>%
  ungroup()

ggplot(
  configuration_binary,
  aes(
    x = configuration,
    y = share,
    fill = binary_outcome
  )
) +
  geom_col(position = "fill") +
  facet_wrap(~ phase) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Outcome Proportions by Experimental Configuration",
    x = NULL,
    y = "Share of executions",
    fill = "Outcome"
  ) +
  theme(
    axis.text.x = element_text(
      angle = 25,
      hjust = 1
    )
  )
```

```{r}
configuration_summary <- main_results %>%
  group_by(
    phase,
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    successes = sum(binary_outcome == "Success"),
    failures = sum(binary_outcome == "Failure"),
    success_rate = successes / runs,
    .groups = "drop"
  )

ggplot(
  configuration_summary,
  aes(
    x = factor(initial_nodes),
    y = factor(max_neighbors),
    fill = success_rate
  )
) +
  geom_tile(
    color = "white",
    linewidth = 0.6
  ) +
  geom_text(
    aes(
      label = paste0(
        scales::percent(success_rate, accuracy = 1),
        "\n",
        "n = ", runs
      )
    ),
    size = 3.3
  ) +
  facet_wrap(~ phase) +
  scale_fill_gradient(
    low = "yellow",
    high = "lightgreen",
    limits = c(0, 1),
    labels = scales::percent,
    name = "Success rate"
  ) +
  labs(
    title = "Success Rate by Experimental Configuration",
    subtitle = paste(
      "Color represents the effective success rate;",
      "labels show the success percentage and number of executions"
    ),
    x = "Initial node count",
    y = "Maximum neighbors"
  ) +
  theme(
    panel.grid = element_blank(),
    legend.position = "right"
  )
```

# Failure Severity

This section shows how many nodes remained deficient when a main phase did not succeed.

```{r failure-severity, fig.height=5.5}
failure_severity <- main_results %>%
  filter(!effective_success) %>%
  count(
    phase,
    failed_nodes_count,
    name = "runs"
  )

if (nrow(failure_severity) == 0) {
  cat("No effective failures were recorded in Phases 1-5.")
} else {
  ggplot(
    failure_severity,
    aes(
      x = factor(failed_nodes_count),
      y = runs,
      fill = phase
    )
  ) +
    geom_col(position = "dodge") +
    labs(
      title = "Failure Severity by Main Phase",
      x = "Number of failed/deficient nodes remaining",
      y = "Number of executions",
      fill = "Phase"
    )
}
```

# Timeout-With-Zero-Failure Anomalies

These rows reported a timeout even though zero nodes were still below `MAX_NEIGHBORS`. They are counted as successes for reliability, but should be investigated as evaluation-script or event-ordering errors.

```{r anomaly-summary}
anomalies <- results %>%
  filter(timeout_zero_anomaly) %>%
  transmute(
    timestamp,
    phase,
    original_status = status,
    elapsed_seconds = round(elapsed_seconds, 3),
    initial_nodes,
    max_neighbors,
    failed_nodes_count,
    details
  )

anomaly_count_by_phase <- anomalies %>%
  count(phase, name = "anomaly_count")

cat(
  "Total timeout-with-zero-failure anomalies: **",
  nrow(anomalies),
  "**.\n\n",
  sep = ""
)

if (nrow(anomaly_count_by_phase) > 0) {
  knitr::kable(
    anomaly_count_by_phase,
    caption = "Anomaly count by phase"
  )
}

if (nrow(anomalies) > 0) {
  knitr::kable(
    anomalies,
    caption = "Rows classified as timeout-with-zero-failure anomalies"
  )
}
```

## Likely Meaning of the Anomaly

A likely explanation is a race between the timeout check and the final topology observation:

- the phase timeout expires;
- the script marks the phase as `PARTIAL`;
- a final node-state query sees zero deficient nodes; and
- both results are written into the same row.

Another possibility is that the script calculates `timed_out` before its last successful convergence check. The evaluation code should ideally perform one final state check immediately after the wait ends and derive both `status` and `failed_nodes_count` from that same snapshot.

# Recommended Metrics for the Research Report

The generated figures already cover reliability, failure severity, recovery effectiveness, configuration effects, timing distributions, and performance trends. For the final research report, the most useful reported metrics are:

1.  **Phase success rate** after applying the documented anomaly rule.
2.  **Median and 95th-percentile completion time**, rather than only the average.
3.  **Failure severity**, measured by the number of nodes still deficient at timeout.
4.  **Phase R recovery success rate**, grouped by the phase that triggered recovery.
5.  **Configuration-specific success rate**, especially when increasing `initial_nodes` or `max_neighbors`.
6.  **Run-order timing trends**, which may reveal CPU contention when many Java processes run on one machine.
7.  **Anomaly count**, kept separate from protocol failures because it represents measurement quality.

# Reproducibility Information

```{r session-info}
sessionInfo()
```
