---
title: "Evaluation Statistics"
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex: false
geometry: margin=1in
fontsize: 11pt
header-includes:
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  #fig.width = 7.4,
  #fig.height = 4.8,
  fig.pos = "H",
  dev = "pdf",
  fig.path = "figures/"
)

library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(patchwork)

options(knitr.kable.NA = "")
```

# Setup

## Import and Filter Data

```{r data}
candidate_files <- c(
  "results.csv",
  "evaluation_results.csv"
)

data_file <- candidate_files[file.exists(candidate_files)][1]

if (is.na(data_file)) {
  stop("Place results.csv in the same directory as this Rmd file.")
}

STATUS_LEVELS <- c(
  "PASS",
  "TIMEOUT",
  "FAIL"
)

PRIMARY_PHASES <- c(
  "Phase 1",
  "Phase 3",
  "Phase 4",
  "Phase 5"
)

RECOVERY_PHASES <- c(
  "R1",
  "R3",
  "R4",
  "R5"
)

DIRECT_STABILITY_PHASES <- c(
  "S1",
  "S3",
  "S4",
  "S5"
)

STABILITY_PHASES <- c(
  DIRECT_STABILITY_PHASES,
  "SR"
)

# Entries may exceed the configured timeout by up to 10 seconds.
TIMEOUT_GRACE_SECONDS <- 30

# Recovery entries below 10 seconds are treated as not executed.
MINIMUM_RECOVERY_SECONDS <- 10

PHASE_TIMEOUT_SECONDS <- c(
  "Phase 1" = 120,
  "Phase 2.1" = 120,
  "Phase 2.2" = 120,
  "Phase 3" = 180,
  "Phase 4" = 120,
  "Phase 5" = 180,
  "R1" = 120,
  "R3" = 120,
  "R4" = 120,
  "R5" = 120
)

raw_results <- read_csv(
  data_file,
  show_col_types = FALSE,
  progress = FALSE
) %>%
  mutate(
    row_id = row_number(),
    run_id = cumsum(phase == "Phase 1"),
    timestamp = ymd_hms(
      timestamp,
      quiet = TRUE
    ),
    elapsed_seconds = elapsed_ms / 1000
  ) %>%
  group_by(run_id) %>%
  arrange(
    row_id,
    .by_group = TRUE
  ) %>%
  mutate(
    recovery_context = if_else(
      phase %in% RECOVERY_PHASES,
      phase,
      NA_character_
    )
  ) %>%
  fill(
    recovery_context,
    .direction = "down"
  ) %>%
  mutate(
    # Associates each SR row with the recovery phase that preceded it.
    sr_parent_recovery = if_else(
      phase == "SR",
      recovery_context,
      NA_character_
    ),

    timeout_seconds = unname(
      PHASE_TIMEOUT_SECONDS[phase]
    ),

    effective_timeout_seconds = if_else(
      !is.na(timeout_seconds),
      timeout_seconds + TIMEOUT_GRACE_SECONDS,
      NA_real_
    ),

    exceeds_timeout = (
      !is.na(effective_timeout_seconds) &
        elapsed_seconds > effective_timeout_seconds
    ),

    recovery_not_run = (
      phase %in% RECOVERY_PHASES &
        elapsed_seconds < MINIMUM_RECOVERY_SECONDS
    ),

    # Identifies the main phase to which an R, S, or SR row belongs.
    dependency_primary_phase = case_when(
      phase %in% c("R1", "S1") ~
        "Phase 1",

      phase %in% c("R3", "S3") ~
        "Phase 3",

      phase %in% c("R4", "S4") ~
        "Phase 4",

      phase %in% c("R5", "S5") ~
        "Phase 5",

      phase == "SR" ~ recode(
        sr_parent_recovery,
        "R1" = "Phase 1",
        "R3" = "Phase 3",
        "R4" = "Phase 4",
        "R5" = "Phase 5",
        .default = NA_character_
      ),

      TRUE ~ NA_character_
    )
  ) %>%
  ungroup()

# A main phase beyond its timeout plus grace period is invalid.
# Its directly dependent R and S rows are removed as well.
invalid_primary_phases <- raw_results %>%
  filter(
    exceeds_timeout,
    phase %in% PRIMARY_PHASES
  ) %>%
  transmute(
    run_id,
    dependency_primary_phase = phase,
    invalid_primary = TRUE
  ) %>%
  distinct()

# A recovery row is invalid when it exceeds the timeout plus grace
# period or lasts less than 10 seconds. Its SR row is removed as well.
invalid_recovery_phases <- raw_results %>%
  filter(
    phase %in% RECOVERY_PHASES,
    exceeds_timeout | recovery_not_run
  ) %>%
  transmute(
    run_id,
    sr_parent_recovery = phase,
    invalid_recovery = TRUE
  ) %>%
  distinct()

filtered_results <- raw_results %>%
  left_join(
    invalid_primary_phases,
    by = c(
      "run_id",
      "dependency_primary_phase"
    )
  ) %>%
  left_join(
    invalid_recovery_phases,
    by = c(
      "run_id",
      "sr_parent_recovery"
    )
  ) %>%
  mutate(
    invalid_primary = replace_na(
      invalid_primary,
      FALSE
    ),

    invalid_recovery = replace_na(
      invalid_recovery,
      FALSE
    ),

    remove_due_to_primary = invalid_primary,

    remove_due_to_recovery = (
      phase == "SR" &
        invalid_recovery
    ),

    remove_row = (
      exceeds_timeout |
        recovery_not_run |
        remove_due_to_primary |
        remove_due_to_recovery
    ),

    removal_reason = case_when(
      recovery_not_run ~
        "Recovery execution below 10 seconds; treated as not run",

      exceeds_timeout ~
        "Elapsed time exceeded configured timeout plus grace period",

      remove_due_to_primary ~
        "Dependent recovery or stability entry removed with primary phase",

      remove_due_to_recovery ~
        "SR entry removed with invalid recovery phase",

      TRUE ~
        "Kept"
    )
  )

removed_entries <- filtered_results %>%
  filter(remove_row)

results <- filtered_results %>%
  filter(!remove_row) %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

# One valid row for each main phase that can trigger recovery.
main_phase_rows <- results %>%
  filter(phase %in% PRIMARY_PHASES) %>%
  transmute(
    run_id,

    phase_group = phase,

    primary_status = as.character(status)
  ) %>%
  distinct(
    run_id,
    phase_group,
    .keep_all = TRUE
  )

# The direct stability check determines whether a main-phase success
# remained valid without replacement-based recovery.
direct_stability_rows <- results %>%
  filter(phase %in% DIRECT_STABILITY_PHASES) %>%
  transmute(
    run_id,

    phase_group = recode(
      phase,
      "S1" = "Phase 1",
      "S3" = "Phase 3",
      "S4" = "Phase 4",
      "S5" = "Phase 5"
    ),

    direct_stability_status = as.character(status)
  ) %>%
  distinct(
    run_id,
    phase_group,
    .keep_all = TRUE
  )

# Only recovery rows that survived all filtering are valid attempts.
# These same rows are used by the outcome tables, recovery charts,
# and recovery summary table.
valid_recovery_rows <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  transmute(
    run_id,

    phase_group = recode(
      phase,
      "R1" = "Phase 1",
      "R3" = "Phase 3",
      "R4" = "Phase 4",
      "R5" = "Phase 5"
    ),

    recovery_phase = phase,
    recovery_status = as.character(status)
  ) %>%
  distinct(
    run_id,
    phase_group,
    .keep_all = TRUE
  )

# Phase 2 has two required measurements. A run is included in the
# Phase 2 outcome data only when both Phase 2.1 and Phase 2.2 remain.
# An incomplete pair is therefore represented as "Not run" later.
phase_2_rows <- results %>%
  filter(
    phase %in% c(
      "Phase 2.1",
      "Phase 2.2"
    )
  ) %>%
  group_by(run_id) %>%
  summarise(
    phase_2_1_present = any(
      phase == "Phase 2.1"
    ),

    phase_2_2_present = any(
      phase == "Phase 2.2"
    ),

    phase_2_1_pass = any(
      phase == "Phase 2.1" &
        status == "PASS"
    ),

    phase_2_2_pass = any(
      phase == "Phase 2.2" &
        status == "PASS"
    ),

    .groups = "drop"
  ) %>%
  filter(
    phase_2_1_present,
    phase_2_2_present
  ) %>%
  transmute(
    run_id,
    phase_group = "Phase 2",

    primary_status = if_else(
      phase_2_1_pass &
        phase_2_2_pass,
      "PASS",
      "TIMEOUT"
    ),

    direct_stability_status = NA_character_
  )

phase_outcomes <- bind_rows(
  main_phase_rows %>%
    left_join(
      direct_stability_rows,
      by = c(
        "run_id",
        "phase_group"
      )
    ),

  phase_2_rows
) %>%
  left_join(
    valid_recovery_rows,
    by = c(
      "run_id",
      "phase_group"
    )
  ) %>%
  mutate(
    recovery_ran = !is.na(
      recovery_phase
    ),

    direct_success = case_when(
      phase_group == "Phase 2" ~
        primary_status == "PASS",

      TRUE ~
        primary_status == "PASS" &
          coalesce(
            direct_stability_status == "PASS",
            FALSE
          )
    ),

    # A valid recovery attempt takes precedence over the direct result.
    # This correctly handles recovery triggered by a failed S check
    # even when the preceding main phase itself recorded PASS.
    outcome = case_when(
      recovery_status == "PASS" ~
        "Success (with recovery)",

      recovery_ran ~
        "Failure (with recovery)",

      direct_success ~
        "Success (no recovery)",

      TRUE ~
        "Failure (no recovery)"
    ),

    final_outcome = if_else(
      outcome %in% c(
        "Success (no recovery)",
        "Success (with recovery)"
      ),
      "Success",
      "Failure"
    ),

    phase_group = factor(
      phase_group,
      levels = c(
        "Phase 1",
        "Phase 2",
        "Phase 3",
        "Phase 4",
        "Phase 5"
      )
    ),

    outcome = factor(
      outcome,
      levels = c(
        "Success (no recovery)",
        "Success (with recovery)",
        "Failure (no recovery)",
        "Failure (with recovery)"
      )
    ),

    final_outcome = factor(
      final_outcome,
      levels = c(
        "Success",
        "Failure"
      )
    )
  )

# Guard against the exact inconsistency where the outcome table and
# recovery table count different sets of valid recovery attempts.
valid_recovery_attempt_count <- valid_recovery_rows %>%
  summarise(attempts = n()) %>%
  pull(attempts)

classified_recovery_attempt_count <- phase_outcomes %>%
  filter(recovery_ran) %>%
  summarise(attempts = n()) %>%
  pull(attempts)

if (
  valid_recovery_attempt_count !=
    classified_recovery_attempt_count
) {
  stop(
    paste(
      "Recovery-attempt mismatch:",
      valid_recovery_attempt_count,
      "valid R rows but",
      classified_recovery_attempt_count,
      "recovery-classified phase outcomes."
    )
  )
}
```

```{r}
middle_focus_transform <- function( center = 35, spread = 15 ) { scales::new_transform( name = "middle_focus", transform = function(x) { plogis((x - center) / spread) }, inverse = function(x) { center + spread * qlogis(x) }, domain = c(-Inf, Inf) ) }
```

```{r timeout-filter-summary}
timeout_filter_summary <- removed_entries %>%
  count(
    phase,
    removal_reason,
    name = "removed_entries"
  ) %>%
  arrange(phase, removal_reason)

kable(
  timeout_filter_summary,
  caption = "Entries excluded by timeout, minimum-duration, and dependency filtering.",
  align = c("l", "l", "r")
)
```

## Theme Settings

```{r theme}
COLOR_PASS <- "#C6FFDD"
COLOR_TIMEOUT <- "#FBD786"
COLOR_FAIL <- "#f7797d"

VALUE_GRADIENT <- c(
  low = "#fbc7d4",
  high = "#9796f0"
)

SUCCESS_GRADIENT <- c(
  COLOR_FAIL,
  COLOR_TIMEOUT,
  COLOR_PASS
)

STATUS_COLORS <- c(
  "PASS" = COLOR_PASS,
  "TIMEOUT" = COLOR_TIMEOUT,
  "FAIL" = COLOR_FAIL
)

STATUS_LABELS <- c(
  "PASS" = "Pass",
  "TIMEOUT" = "Timeout",
  "FAIL" = "Fail"
)

STATUS_SHAPES <- c(
  "PASS" = 21,
  "TIMEOUT" = 24,
  "FAIL" = 22
)

FINAL_OUTCOME_COLORS <- c(
  "Success" = COLOR_PASS,
  "Failure" = COLOR_FAIL
)

DETAILED_OUTCOME_COLORS <- c(
  "Success (no recovery)" = "#C6FFDD",
  "Success (with recovery)" = "#96e6b3",
  "Failure (no recovery)" = "#FBD786",
  "Failure (with recovery)" = "#f7797d"
)

ARBITRARY_COLORS <- colorRampPalette(
  c(
    "#ff75c3",
    "#ffa647",
    "#ffe83f",
    "#9fff5b",
    "#70e2ff",
    "#cd93ff"
  )
)(10)

theme_set(
  theme_minimal(
    base_size = 11,
    base_family = "serif"
  ) +
    theme(
      text = element_text(family = "serif"),
      plot.title = element_text(
        face = "bold",
        size = 13,
        hjust = 0.5
      ),
      plot.subtitle = element_text(
        size = 9.5,
        hjust = 0.5,
        margin = margin(b = 8)
      ),
      panel.grid.minor = element_blank(),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      axis.title = element_text(face = "bold"),
      strip.text = element_text(face = "bold"),
      plot.caption = element_text(
        size = 8.5,
        hjust = 0
      ),
      plot.margin = margin(9, 9, 9, 9)
    )
)
```

# Success Rates

```{r}
runs_by_phase <- results %>%
  count(phase, name = "number_of_runs") %>%
  mutate(
    phase = factor(
      phase,
      levels = c(
        "Phase 1",
        "S1",
        "R1",
        "Phase 2.1",
        "Phase 2.2",
        "Phase 3",
        "S3",
        "R3",
        "Phase 4",
        "S4",
        "R4",
        "Phase 5",
        "S5",
        "R5",
        "SR"
      )
    )
  ) %>%
  arrange(phase)

kable(
  runs_by_phase,
  caption = "Number of Valid Runs Recorded for Each Evaluation Phase",
  col.names = c(
    "Phase",
    "Number of runs"
  ),
  align = c("l", "r")
)
```

## Final Outcome by Main Phase

```{r final-success-rate-chart}
baseline_runs <- phase_outcomes %>%
  filter(phase_group == "Phase 1") %>%
  summarise(runs = n_distinct(run_id)) %>%
  pull(runs)

final_outcome_levels <- c(
  "Success",
  "Failure",
  "Not run"
)

observed_final_outcomes <- phase_outcomes %>%
  mutate(
    phase_group = as.character(phase_group),
    final_outcome = as.character(final_outcome)
  ) %>%
  count(
    phase_group,
    final_outcome,
    name = "runs"
  )

not_run_counts <- tibble(
  phase_group = c(
    "Phase 1",
    "Phase 2",
    "Phase 3",
    "Phase 4",
    "Phase 5"
  )
) %>%
  left_join(
    observed_final_outcomes %>%
      group_by(phase_group) %>%
      summarise(
        observed_runs = sum(runs),
        .groups = "drop"
      ),
    by = "phase_group"
  ) %>%
  mutate(
    observed_runs = replace_na(observed_runs, 0L),
    final_outcome = "Not run",
    runs = baseline_runs - observed_runs
  ) %>%
  select(
    phase_group,
    final_outcome,
    runs
  )

final_success_chart_data <- bind_rows(
  observed_final_outcomes,
  not_run_counts
) %>%
  complete(
    phase_group = c(
      "Phase 1",
      "Phase 2",
      "Phase 3",
      "Phase 4",
      "Phase 5"
    ),
    final_outcome = final_outcome_levels,
    fill = list(runs = 0)
  ) %>%
  mutate(
    phase_group = factor(
      phase_group,
      levels = c(
        "Phase 1",
        "Phase 2",
        "Phase 3",
        "Phase 4",
        "Phase 5"
      )
    ),
    final_outcome = factor(
      final_outcome,
      levels = final_outcome_levels
    ),
    share = runs / baseline_runs,
    label = if_else(
      runs > 0 & share >= 0.04,
      percent(share, accuracy = 0.1),
      ""
    )
  )

FINAL_OUTCOME_COLORS_WITH_NOT_RUN <- c(
  FINAL_OUTCOME_COLORS,
  "Not run" = "gray70"
)

ggplot(
  final_success_chart_data,
  aes(
    x = phase_group,
    y = share,
    fill = final_outcome
  )
) +
  geom_col(
    width = 0.7,
    color = "grey25",
    linewidth = 0.1,
    position = position_stack(reverse = TRUE)
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(
      vjust = 0.5,
      reverse = TRUE
    ),
    family = "serif",
    size = 3.1
  ) +
  scale_fill_manual(
    values = FINAL_OUTCOME_COLORS_WITH_NOT_RUN,
    limits = final_outcome_levels,
    labels = c(
      "Success" = "Successful",
      "Failure" = "Unsuccessful",
      "Not run" = "Not executed"
    ),
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Success Rate by Main Evaluation Phase",
    x = "Evaluation phase",
    y = "Share of runs",
    fill = "Outcome"
  )
```

## Direct, Recovered, Failed, and Not-Run Outcomes

```{r detailed-outcome-chart, fig.width = 7.4}
phase_levels <- c(
  "Phase 1",
  "Phase 2",
  "Phase 3",
  "Phase 4",
  "Phase 5"
)

outcome_levels <- c(
  "Success (no recovery)",
  "Success (with recovery)",
  "Failure (no recovery)",
  "Failure (with recovery)",
  "Not run"
)

# Phase 1 is the baseline number of experimental runs.
baseline_runs <- phase_outcomes %>%
  filter(phase_group == "Phase 1") %>%
  summarise(runs = n_distinct(run_id)) %>%
  pull(runs)

observed_outcome_counts <- phase_outcomes %>%
  mutate(
    phase_group = as.character(phase_group),
    outcome = as.character(outcome)
  ) %>%
  count(
    phase_group,
    outcome,
    name = "runs"
  )

not_run_counts <- tibble(
  phase_group = phase_levels
) %>%
  left_join(
    observed_outcome_counts %>%
      group_by(phase_group) %>%
      summarise(
        observed_runs = sum(runs),
        .groups = "drop"
      ),
    by = "phase_group"
  ) %>%
  mutate(
    observed_runs = replace_na(observed_runs, 0L),
    runs = baseline_runs - observed_runs,
    outcome = "Not run"
  ) %>%
  select(
    phase_group,
    outcome,
    runs
  )

detailed_outcome_chart_data <- bind_rows(
  observed_outcome_counts,
  not_run_counts
) %>%
  complete(
    phase_group = phase_levels,
    outcome = outcome_levels,
    fill = list(runs = 0)
  ) %>%
  mutate(
    phase_group = factor(
      phase_group,
      levels = phase_levels
    ),
    outcome = factor(
      outcome,
      levels = outcome_levels
    ),
    share = runs / baseline_runs,
    label = if_else(
      runs > 0 & share >= 0.04,
      paste0(
        percent(share, accuracy = 0.1)
      ),
      ""
    )
  )

DETAILED_OUTCOME_COLORS_WITH_NOT_RUN <- c(
  DETAILED_OUTCOME_COLORS,
  "Not run" = "gray70"
)

ggplot(
  detailed_outcome_chart_data,
  aes(
    x = phase_group,
    y = share,
    fill = outcome
  )
) +
  geom_col(
    width = 0.7,
    color = "grey25",
    linewidth = 0.25,
    position = position_stack(reverse = TRUE)
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(
      vjust = 0.5,
      reverse = TRUE
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_manual(
    values = DETAILED_OUTCOME_COLORS_WITH_NOT_RUN,
    limits = outcome_levels,
    labels = c(
      "Success (no recovery)" =
        "Success",
      "Success (with recovery)" =
        "Success after recovery",
      "Failure (no recovery)" =
        "Failure without recovery",
      "Failure (with recovery)" =
        "Recovery failed",
      "Not run" =
        "Not executed"
    ),
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = paste(
      "Detailed Success, Failure, and Non-Execution Rate",
      "by Evaluation Phase"
    ),
    x = "Evaluation phase",
    y = "Share of runs",
    fill = "Outcome"
  )
```

```{r success-rate-table}
success_rate_table <- detailed_outcome_chart_data %>%
  select(
    phase_group,
    outcome,
    runs
  ) %>%
  pivot_wider(
    names_from = outcome,
    values_from = runs,
    values_fill = 0
  ) %>%
  arrange(phase_group)

kable(
  success_rate_table,
  caption = "Run counts by phase outcome, including phases that were not executed.",
  align = c(
    "l",
    "r",
    "r",
    "r",
    "r",
    "r"
  )
)
```

# Final Success Rate by Input Variables

## Phase 1: Initial Network Formation

```{r phase1-input-chart, fig.width = 8}
phase1_input_data <- results %>%
  filter(phase == "Phase 1") %>%
  select(
    run_id,
    initial_nodes,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 1") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase1_input_plot <- ggplot(
  phase1_input_data,
  aes(
    x = initial_nodes,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(9, 17),
    breaks = c(1, 20, 40)
  ) +
  scale_x_continuous(
    breaks = breaks_pretty(10), expand = expansion(add = c(0.6, 0.8))
  ) +
  scale_y_continuous(
    breaks = breaks_pretty(), expand = expansion(add = c(0.8, 0.6))
  ) +
  labs(
    title = paste(
      "Phase 1: Final Success Rate by Network Size and Neighbor Limit"
    ),
    x = "Initial node count",
    y = "Maximum neighbors",
    fill = "Final success rate",
    size = "Runs count"
  )

phase1_input_plot
```

## Phase 3: Single-Node Failure Repair

```{r phase3-input-chart, fig.width = 8}
phase3_input_data <- results %>%
  filter(phase == "Phase 3") %>%
  select(
    run_id,
    initial_nodes,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 3") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase3_input_plot <- ggplot(
  phase3_input_data,
  aes(
    x = initial_nodes,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(9, 17),
    breaks = c(1, 20, 40)
  ) +
  scale_x_continuous(
    breaks = breaks_pretty(10), expand = expansion(add = c(0.6, 0.8))
  ) +
  scale_y_continuous(
    breaks = breaks_pretty(), expand = expansion(add = c(0.8, 0.6))
  ) +
  labs(
    title = paste(
      "Phase 3: Final Success Rate by Network Size and Neighbor Limit"
    ),
    x = "Initial node count",
    y = "Maximum neighbors",
    fill = "Final success rate",
    size = "Runs count"
  )

phase3_input_plot
```

## Phase 4: Adding Nodes

```{r phase4-input-chart}
phase4_input_data <- results %>%
  filter(phase == "Phase 4") %>%
  select(
    run_id,
    added_node_count,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 4") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    added_node_count,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase4_input_plot <- ggplot(
  phase4_input_data,
  aes(
    x = added_node_count,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(9, 17),
    breaks = c(1, 30, 60)
  ) +
  scale_x_continuous(
    breaks = breaks_pretty(), expand = expansion(add = c(0.6, 0.6))
  ) +
  scale_y_continuous(
    breaks = breaks_pretty(), expand = expansion(add = c(0.8, 0.8))
  ) +
  labs(
    title = paste(
      "Phase 4: Final Success Rate by Added Nodes and Neighbor Limit"
    ),
    x = "Added nodes",
    y = "Maximum neighbors",
    fill = "Final success rate",
    size = "Runs count"
  )

phase4_input_plot
```

## Phase 5: Removing Multiple Nodes

```{r phase5-input-chart, fig.width = 7}
phase5_input_data <- results %>%
  filter(phase == "Phase 5") %>%
  select(
    run_id,
    removed_node_count,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 5") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    removed_node_count,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase5_input_plot <- ggplot(
  phase5_input_data,
  aes(
    x = removed_node_count,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(9, 17),
    breaks = c(1, 30, 60)
  ) +
  scale_x_continuous(
    breaks = breaks_pretty(), expand = expansion(add = c(0.6, 0.6))
  ) +
  scale_y_continuous(
    breaks = breaks_pretty(), expand = expansion(add = c(0.8, 0.6))
  ) +
  labs(
    title = paste(
      "Phase 5: Final Success Rate by Removed Nodes and Neighbor Limit"
    ),
    x = "Removed nodes",
    y = "Maximum neighbors",
    fill = "Final success rate",
    size = "Runs count"
  )

phase5_input_plot
```

## Combined Input-Variable Comparison

```{r combined-input-chart, fig.width=10, fig.height=8.8}
(
  phase1_input_plot +
    phase3_input_plot +
    phase4_input_plot +
    phase5_input_plot
) +
  plot_layout(
    ncol = 2,
    guides = "collect"
  ) +
  plot_annotation(
    title = paste(
      "Final Success Rates Across Tested Network Sizes,",
      "Neighbor Limits, Node Additions, and Node Removals"
    ),
    subtitle = paste(
      "Final success includes successful replacement-based recovery;",
      "bubble size represents the number of repeated runs."
    ),
    theme = theme(
      plot.title = element_text(
        family = "serif",
        face = "bold",
        size = 14,
        hjust = 0.5
      ),
      plot.subtitle = element_text(
        family = "serif",
        size = 10,
        hjust = 0.5
      )
    )
  ) &
  theme(
    text = element_text(family = "serif"),
    legend.position = "bottom"
  )
```

# Stability Checks

```{r stability-success-chart}
stability_labels <- c(
  "S1" = "After initial formation (S1)",
  "S3" = "After single-failure repair (S3)",
  "S4" = "After adding nodes (S4)",
  "S5" = "After multiple failures (S5)",
  "SR" = "After replacement recovery (SR)"
)

stability_chart_data <- results %>%
  filter(phase %in% STABILITY_PHASES) %>%
  mutate(
    phase = factor(
      phase,
      levels = STABILITY_PHASES
    ),
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  ) %>%
  count(
    phase,
    status,
    name = "runs"
  ) %>%
  complete(
    phase = factor(
      STABILITY_PHASES,
      levels = STABILITY_PHASES
    ),
    status = factor(
      STATUS_LEVELS,
      levels = STATUS_LEVELS
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(phase) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0,
      paste0(
        percent(share, accuracy = 0.1),
        "\n(n = ", runs, ")"
      ),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  stability_chart_data,
  aes(
    x = phase,
    y = share,
    fill = status
  )
) +
  geom_col(
    width = 0.65,
    color = "grey25",
    linewidth = 0.25
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    family = "serif",
    size = 3
  ) +
  coord_flip() +
  scale_x_discrete(
    labels = stability_labels,
    limits = rev(STABILITY_PHASES)
  ) +
  scale_fill_manual(
    values = STATUS_COLORS,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Outcomes of the 10-Second Post-Phase Stability Checks",
    subtitle = paste(
      "Each bar shows whether the topology remained valid for the full",
      "10-second observation window after the named operation."
    ),
    x = "Stability check and preceding operation",
    y = "Share of stability checks",
    fill = "Recorded status"
  )
```

# Failure Detection Time

```{r phase2-time-chart}
phase2_time_data <- results %>%
  filter(
    phase %in% c("Phase 2.1", "Phase 2.2")
  ) %>%
  mutate(
    detection_milestone = factor(
      phase,
      levels = c(
        "Phase 2.1",
        "Phase 2.2"
      ),
      labels = c(
        "First failure report\n(Phase 2.1)",
        "All expected failure reports\n(Phase 2.2)"
      )
    ),
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase2_time_data,
  aes(
    x = detection_milestone,
    y = elapsed_seconds
  )
) +
  geom_boxplot(
    width = 0.55,
    fill = "white",
    color = "grey35",
    linewidth = 0.45,
    outlier.shape = NA,
    alpha = 0.55
  ) +
  geom_jitter(
    aes(fill = status),
    shape = 21,
    width = 0.12,
    stroke = 0.35,
    height = 0,
    size = 2.1,
    alpha = 0.8
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey40"
  ) +
  scale_fill_manual(
    values = c(
      "PASS" = COLOR_PASS,
      "TIMEOUT" = COLOR_TIMEOUT,
      "FAIL" = COLOR_FAIL
    ),
    limits = STATUS_LEVELS,
    breaks = c("PASS", "TIMEOUT"),
    labels = STATUS_LABELS[c("PASS", "TIMEOUT")],
    drop = FALSE
  ) +
  scale_y_continuous(
    transform = middle_focus_transform(
      center = 20,
      spread = 15
    ),
    breaks = c(
      0,5,
      10,15,
      20,
      30,
      40,
      50,
      60,
      120
    ),
    limits = c(0, 130),
    expand = expansion(
      mult = c(0.02, 0.04)
    )
  ) +
  labs(
    title = "Phase 2: Detection Time for First Report and All Expected Reporting",
    x = "Failure-detection milestone",
    y = "Elapsed time",
    color = "Recorded status"
  )
```

# Main-Phase Completion Time and Input Effects

## Phase 1: Initial Network Formation

```{r phase1-time-impact-chart}
phase1_time_data <- results %>%
  filter(phase == "Phase 1") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase1_time_data,
  aes(
    x = initial_nodes,
    y = elapsed_seconds
  )
) +
  geom_boxplot( data = phase1_time_data %>% filter(status == "PASS"),aes( group = factor(initial_nodes) ), width = 0.8, fill = "white", color = "grey35", linewidth = 0.45, alpha = 0.45, outlier.shape = NA ) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.4,
      height = 0
    ),
    size = 2.5,
    color = "grey15",
    stroke = 0.2,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    breaks = c("PASS", "TIMEOUT"),
    labels = STATUS_LABELS[c("PASS", "TIMEOUT")],
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = breaks_pretty()
  ) + scale_y_continuous( transform = middle_focus_transform( center = 20, spread = 15 ), breaks = c( 0, 5, 15, 20, 25, 35, 60, 120 ), limits = c(5, 130), expand = expansion(mult = c(0.02, 0.04)) ) +
  guides( fill = guide_colorbar(order = 1), shape = guide_legend(order = 2) 
          ) +
  labs(
    title = "Phase 1: Execution Time by Initial Node Count and Neighbor Limit",
    x = "Initial node count",
    y = "Time",
    fill = "Maximum neighbors",
    shape = "Recorded status"
  )
```

## Phase 3: Repair After One Node Failure

```{r phase3-time-impact-chart}
phase3_time_data <- results %>%
  filter(phase == "Phase 3") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase3_time_data,
  aes(
    x = initial_nodes,
    y = elapsed_seconds
  )
) +
  geom_boxplot(
    data = phase3_time_data %>%
      filter(status == "PASS"),
    aes(
      group = factor(initial_nodes)
    ),
    width = 0.8,
    fill = "white",
    color = "grey35",
    linewidth = 0.45,
    alpha = 0.45,
    outlier.shape = NA
  ) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.4,
      height = 0
    ),
    size = 2.5,
    color = "grey15",
    stroke = 0.2,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 180,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    breaks = c("PASS", "TIMEOUT"),
    labels = STATUS_LABELS[c("PASS", "TIMEOUT")],
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = breaks_pretty()
  ) + scale_y_continuous( transform = middle_focus_transform( center = 50, spread = 40 ), breaks = c( 0, 20,30, 40, 50, 60, 80, 120, 180), limits = c(0, 200), expand = expansion(mult = c(0.02, 0.04)) )+
  guides( fill = guide_colorbar(order = 1), shape = guide_legend(order = 2) 
  ) +
  labs(
    title = "Phase 3: Execution Time by Initial Node Count and Neighbor Limit",
    x = "Initial node count",
    y = "Time",
    fill = "Maximum neighbors",
    shape = "Recorded status"
  )
```

## Phase 4: Adding Nodes

```{r phase4-time-impact-chart}
phase4_time_data <- results %>%
  filter(phase == "Phase 4") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase4_time_data,
  aes(
    x = added_node_count,
    y = elapsed_seconds
  )
) +
  geom_boxplot(
    data = phase4_time_data %>%
      filter(status == "PASS"),
    aes(
      group = factor(added_node_count)
    ),
    width = 0.8,
    fill = "white",
    color = "grey35",
    linewidth = 0.45,
    alpha = 0.45,
    outlier.shape = NA
  ) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.3,
      height = 0
    ),
    size = 2.5,
    color = "grey15",
    stroke = 0.2,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    breaks = c("PASS", "TIMEOUT"),
    labels = STATUS_LABELS[c("PASS", "TIMEOUT")],
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = breaks_pretty()
  ) + scale_y_continuous( transform = middle_focus_transform( center = 20, spread = 15 ), breaks = c( 0, 10, 15, 20, 25, 30, 40, 60,120), limits = c(0, 130), expand = expansion(mult = c(0.02, 0.04)) )+
  guides( fill = guide_colorbar(order = 1), shape = guide_legend(order = 2) 
  ) +
  labs(
    title = "Phase 4: Execution Time by Added Node Count and Neighbor Limit",
    x = "Number of added nodes",
    y = "Time",
    fill = "Maximum neighbors",
    shape = "Recorded status"
  )
```

## Phase 5: Repair After Multiple Node Failures

```{r phase5-time-impact-chart}
phase5_time_data <- results %>%
  filter(phase == "Phase 5") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase5_time_data,
  aes(
    x = removed_node_count,
    y = elapsed_seconds
  )
) +
  geom_boxplot(
    data = phase5_time_data %>%
      filter(status == "PASS"),
    aes(
      group = factor(removed_node_count)
    ),
    width = 0.8,
    fill = "white",
    color = "grey35",
    linewidth = 0.45,
    alpha = 0.45,
    outlier.shape = NA
  ) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.3,
      height = 0
    ),
    size = 2.5,
    color = "grey15",
    stroke = 0.2,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 180,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    breaks = c("PASS", "TIMEOUT"),
    labels = STATUS_LABELS[c("PASS", "TIMEOUT")],
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = c(4, 5, 6, 8, 10, 12)
  ) + scale_y_continuous( transform = middle_focus_transform( center = 75, spread = 40 ), breaks = c( 20, 40, 60, 75, 90, 110, 150, 180), limits = c(20, 200), expand = expansion(mult = c(0.02, 0.04)) )+
  guides( fill = guide_colorbar(order = 1), shape = guide_legend(order = 2) 
  ) +
  labs(
    title = "Phase 5: Execution Time by Removed Node Count and Neighbor Limit",
    x = "Number of removed nodes",
    y = "Time",
    fill = "Maximum neighbors",
    shape = "Recorded status"
  )
```

# Replacement-Based Recovery Completion Time

```{r recovery-time-impact-chart}
recovery_trigger_data <- results %>%
  filter(
    phase %in% c(
      "Phase 1",
      "Phase 3",
      "Phase 4",
      "Phase 5"
    )
  ) %>%
  transmute(
    run_id,
    trigger_phase = phase,
    trigger_problem_count = problem_count,
    trigger_max_neighbors = max_neighbors
  )

recovery_time_data <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  transmute(
    run_id,
    recovery_phase = factor(
      phase,
      levels = RECOVERY_PHASES
    ),
    recovery_status = factor(
      status,
      levels = STATUS_LEVELS
    ),
    elapsed_seconds,
    trigger_phase = recode(
      phase,
      "R1" = "Phase 1",
      "R3" = "Phase 3",
      "R4" = "Phase 4",
      "R5" = "Phase 5"
    )
  ) %>%
  left_join(
    recovery_trigger_data,
    by = c("run_id", "trigger_phase")
  )

recovery_phase_colors <- setNames(
  ARBITRARY_COLORS[c(1, 4, 7, 10)],
  RECOVERY_PHASES
)

recovery_phase_labels <- c(
  "R1" = "R1",
  "R3" = "R3",
  "R4" = "R4",
  "R5" = "R5"
)

ggplot(
  recovery_time_data,
  aes(
    x = trigger_problem_count,
    y = elapsed_seconds
  )
) +
  geom_point(
    aes(
      color = recovery_phase,
      shape = recovery_status,
      size = trigger_max_neighbors
    ),
    position = position_jitter(
      width = 0.12,
      height = 0
    ),
    alpha = 0.82
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_color_manual(
    values = recovery_phase_colors,
    limits = RECOVERY_PHASES,
    labels = recovery_phase_labels,
    drop = FALSE
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_size_continuous(
    range = c(2.5, 5.5),
    breaks = breaks_pretty(n = 4)
  ) +
  scale_x_continuous(
    breaks = breaks_pretty()
  ) +
  labs(
    title = "Replacement-Based Recovery Time by Triggering Operation and Initial Problem Count",
    subtitle = paste(
      "R1, R3, R4, and R5 restart deficient/problematic nodes and wait for a valid topology.",
      "Dashed line: nominal 120-second timeout; dot-dashed line: 130-second exclusion threshold."
    ),
    x = "Deficient or problematic nodes that triggered recovery",
    y = "Replacement-based recovery time (seconds)",
    color = "Recovery trigger",
    shape = "Recorded status",
    size = "Maximum neighbors per node"
  )
```

# Problematic Nodes in Failed Main Phases

## Phase 1: Initial Network Formation

```{r phase1-problem-count-chart, fig.width = 3.5}
phase1_problem_data <- results %>%
  filter(
    phase == "Phase 1",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase1_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 1 initial-network formation",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Deficient Nodes in Failed Phase 1 Initial-Network Formation Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase1_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = breaks_pretty()
    ) +
    scale_y_continuous(
      breaks = breaks_pretty(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Phase 1: Problematic Nodes",
      x = "Problematic nodes",
      y = "Number of failed runs"
    )
}
```

## Phase 3: Repair After One Node Failure

```{r phase3-problem-count-chart, fig.width = 4}
phase3_problem_data <- results %>%
  filter(
    phase == "Phase 3",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase3_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 3 single-node repair",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Deficient Nodes in Failed Single-Node Failure Repair Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase3_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = breaks_pretty()
    ) +
    scale_y_continuous(
      breaks = breaks_pretty(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Phase 3: Problematic Nodes",
      x = "Problematic nodes",
      y = "Number of failed runs"
    )
}
```

## Phase 4: Adding Nodes

```{r phase4-problem-count-chart, fig.width = 3}
phase4_problem_data <- results %>%
  filter(
    phase == "Phase 4",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase4_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 4 node-addition",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Problematic Nodes in Failed Node-Addition Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase4_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = c(1, 2)
    ) +
    scale_y_continuous(
      breaks = breaks_pretty(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Phase 4: Problematic Nodes",
      x = "Problematic nodes",
      y = "Number of failed runs"
    )
}
```

## Phase 5: Repair After Multiple Node Failures

```{r phase5-problem-count-chart}
phase5_problem_data <- results %>%
  filter(
    phase == "Phase 5",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase5_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 5 multiple-node repair",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Problematic Nodes in Failed Multiple-Node Failure Repair Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase5_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = breaks_pretty()
    ) +
    scale_y_continuous(
      breaks = breaks_pretty(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Phase 5: Problematic Nodes",
      x = "Problematic nodes",
      y = "Number of failed runs"
    )
}
```

# Replacement-Based Recovery Success Rates

```{r recovery-success-chart}
recovery_labels <- c(
  "R1" = "R1",
  "R3" = "R3",
  "R4" = "R4",
  "R5" = "R5"
)

recovery_outcome_levels <- c(
  "Success",
  "Failure"
)

recovery_success_data <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  mutate(
    phase = factor(
      phase,
      levels = RECOVERY_PHASES
    ),
    recovery_outcome = if_else(
      status == "PASS",
      "Success",
      "Failure"
    ),
    recovery_outcome = factor(
      recovery_outcome,
      levels = recovery_outcome_levels
    )
  ) %>%
  count(
    phase,
    recovery_outcome,
    name = "runs"
  ) %>%
  complete(
    phase = factor(
      RECOVERY_PHASES,
      levels = RECOVERY_PHASES
    ),
    recovery_outcome = factor(
      recovery_outcome_levels,
      levels = recovery_outcome_levels
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(phase) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0 & share >= 0.1,
      paste0(
        percent(share, accuracy = 0.1),
        "\n(n = ", runs, ")"
      ),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  recovery_success_data,
  aes(
    x = phase,
    y = share,
    fill = recovery_outcome
  )
) +
  geom_col(
    width = 0.65,
    color = "grey25",
    linewidth = 0.25
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    family = "serif",
    size = 3
  ) +
  coord_flip() +
  scale_x_discrete(
    labels = recovery_labels,
    limits = rev(RECOVERY_PHASES)
  ) +
  scale_fill_manual(
    values = c(
      "Success" = COLOR_PASS,
      "Failure" = COLOR_FAIL
    ),
    limits = recovery_outcome_levels,
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Success Rate of Recovery Attempts by Triggering Phase",
    x = "Triggering Phase",
    y = "Share of valid recovery attempts",
    fill = "Outcome"
  )
```

```{r recovery-success-table}
recovery_success_summary <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  group_by(phase) %>%
  summarise(
    attempts = n(),
    passes = sum(status == "PASS"),
    timeouts = sum(status == "TIMEOUT"),
    failures = sum(status == "FAIL"),
    success_rate = mean(status == "PASS"),
    .groups = "drop"
  ) %>%
  mutate(
    phase = factor(
      phase,
      levels = RECOVERY_PHASES
    )
  ) %>%
  arrange(phase)

kable(
  recovery_success_summary,
  caption = "Valid replacement-based recovery attempts after timeout filtering.",
  digits = 3,
  align = c("l", "r", "r", "r", "r", "r")
)
```

```{r recovery-success-by-max-neighbors-chart}
recovery_by_neighbors_data <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  mutate(
    phase = factor(
      phase,
      levels = RECOVERY_PHASES
    ),
    max_neighbors = factor(
      max_neighbors,
      levels = sort(unique(max_neighbors))
    ),
    recovery_outcome = if_else(
      status == "PASS",
      "Success",
      "Failure"
    ),
    recovery_outcome = factor(
      recovery_outcome,
      levels = c(
        "Success",
        "Failure"
      )
    )
  ) %>%
  count(
    phase,
    max_neighbors,
    recovery_outcome,
    name = "runs"
  ) %>%
  complete(
    nesting(
      phase,
      max_neighbors
    ),
    recovery_outcome = factor(
      c(
        "Success",
        "Failure"
      ),
      levels = c(
        "Success",
        "Failure"
      )
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(
    phase,
    max_neighbors
  ) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0 & share >= 0.08,
      paste0(
        percent(
          share,
          accuracy = 0.1
        ),
        "\n(n = ",
        runs,
        ")"
      ),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  recovery_by_neighbors_data,
  aes(
    x = max_neighbors,
    y = share,
    fill = recovery_outcome
  )
) +
  geom_col(
    width = 0.7,
    color = "grey25",
    linewidth = 0.25,
    position = position_stack(
      reverse = TRUE
    )
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(
      vjust = 0.5,
      reverse = TRUE
    ),
    family = "serif",
    size = 2.8
  ) +
  facet_wrap(
    ~ phase,
    nrow = 1,
    scales = "free_x"
  ) +
  scale_fill_manual(
    values = c(
      "Success" = COLOR_PASS,
      "Failure" = COLOR_FAIL
    ),
    limits = c(
      "Success",
      "Failure"
    ),
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(
      mult = c(0, 0)
    )
  ) +
  labs(
    title = paste(
      "Recovery Success Rates",
      "by Recovery Phase and Neighbor Limit"
    ),
    x = "Maximum neighbors per node",
    y = "Share of valid recovery attempts",
    fill = "Outcome"
  )
```
