---
title: "Evaluation Statistics"
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex: false
geometry: margin=1in
fontsize: 11pt
header-includes:
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 7.4,
  fig.height = 4.8,
  fig.pos = "H",
  dev = "pdf",
  fig.path = "figures/"
)

library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(patchwork)

options(knitr.kable.NA = "")
```

# Setup

## Import and Filter Data

```{r data}
candidate_files <- c(
  "results.csv",
  "evaluation_results.csv"
)

data_file <- candidate_files[file.exists(candidate_files)][1]

if (is.na(data_file)) {
  stop("Place results.csv in the same directory as this Rmd file.")
}

STATUS_LEVELS <- c("PASS", "TIMEOUT", "FAIL")
RECOVERY_PHASES <- c("R1", "R3", "R4", "R5")
STABILITY_PHASES <- c("S1", "S3", "S4", "S5", "SR")

TIMEOUT_GRACE_SECONDS <- 10

PHASE_TIMEOUT_SECONDS <- c(
  "Phase 1" = 120,
  "Phase 2.1" = 120,
  "Phase 2.2" = 120,
  "Phase 3" = 180,
  "Phase 4" = 120,
  "Phase 5" = 180,
  "R1" = 120,
  "R3" = 120,
  "R4" = 120,
  "R5" = 120
)

raw_results <- read_csv(
  data_file,
  show_col_types = FALSE,
  progress = FALSE
) %>%
  mutate(
    row_id = row_number(),
    run_id = cumsum(phase == "Phase 1"),
    timestamp = ymd_hms(timestamp, quiet = TRUE),
    elapsed_seconds = elapsed_ms / 1000
  ) %>%
  group_by(run_id) %>%
  arrange(row_id, .by_group = TRUE) %>%
  mutate(
    recovery_context = if_else(
      phase %in% RECOVERY_PHASES,
      phase,
      NA_character_
    )
  ) %>%
  fill(recovery_context, .direction = "down") %>%
  mutate(
    sr_parent_recovery = if_else(
      phase == "SR",
      recovery_context,
      NA_character_
    ),
    
    timeout_seconds = unname(
      PHASE_TIMEOUT_SECONDS[phase]
    ),
    
    effective_timeout_seconds = if_else(
      !is.na(timeout_seconds),
      timeout_seconds + TIMEOUT_GRACE_SECONDS,
      NA_real_
    ),
    
    exceeds_timeout = (
      !is.na(effective_timeout_seconds) &
        elapsed_seconds > effective_timeout_seconds
    ),
    
    dependency_primary_phase = case_when(
      phase %in% c("R1", "S1") ~ "Phase 1",
      phase %in% c("R3", "S3") ~ "Phase 3",
      phase %in% c("R4", "S4") ~ "Phase 4",
      phase %in% c("R5", "S5") ~ "Phase 5",
      phase == "SR" ~ recode(
        sr_parent_recovery,
        "R1" = "Phase 1",
        "R3" = "Phase 3",
        "R4" = "Phase 4",
        "R5" = "Phase 5",
        .default = NA_character_
      ),
      TRUE ~ NA_character_
    )
  ) %>%
  ungroup()

invalid_primary_phases <- raw_results %>%
  filter(
    exceeds_timeout,
    phase %in% c(
      "Phase 1",
      "Phase 3",
      "Phase 4",
      "Phase 5"
    )
  ) %>%
  transmute(
    run_id,
    dependency_primary_phase = phase,
    invalid_primary = TRUE
  ) %>%
  distinct()

invalid_recovery_phases <- raw_results %>%
  filter(
    exceeds_timeout,
    phase %in% RECOVERY_PHASES
  ) %>%
  transmute(
    run_id,
    sr_parent_recovery = phase,
    invalid_recovery = TRUE
  ) %>%
  distinct()

filtered_results <- raw_results %>%
  left_join(
    invalid_primary_phases,
    by = c(
      "run_id",
      "dependency_primary_phase"
    )
  ) %>%
  left_join(
    invalid_recovery_phases,
    by = c(
      "run_id",
      "sr_parent_recovery"
    )
  ) %>%
  mutate(
    invalid_primary = replace_na(
      invalid_primary,
      FALSE
    ),
    invalid_recovery = replace_na(
      invalid_recovery,
      FALSE
    ),
    remove_due_to_primary = invalid_primary,
    remove_due_to_recovery = (
      phase == "SR" &
      invalid_recovery
    ),
    remove_row = (
      exceeds_timeout |
      remove_due_to_primary |
      remove_due_to_recovery
    ),
    removal_reason = case_when(
      exceeds_timeout ~
        "Elapsed time exceeded configured timeout",
      remove_due_to_primary ~
        "Dependent R/S entry removed with primary phase",
      remove_due_to_recovery ~
        "SR entry removed with recovery phase",
      TRUE ~ "Kept"
    )
  )

removed_entries <- filtered_results %>%
  filter(remove_row)

results <- filtered_results %>%
  filter(!remove_row) %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

valid_recovery_rows <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  transmute(
    run_id,
    phase_group = recode(
      phase,
      "R1" = "Phase 1",
      "R3" = "Phase 3",
      "R4" = "Phase 4",
      "R5" = "Phase 5"
    ),
    recovery_phase = phase,
    recovery_status = as.character(status)
  )

raw_recovery_attempts <- raw_results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  transmute(
    run_id,
    phase_group = recode(
      phase,
      "R1" = "Phase 1",
      "R3" = "Phase 3",
      "R4" = "Phase 4",
      "R5" = "Phase 5"
    ),
    raw_recovery_phase = phase
  ) %>%
  distinct()

phase_outcomes <- bind_rows(
  results %>%
    filter(phase == "Phase 1") %>%
    transmute(
      run_id,
      phase_group = "Phase 1",
      primary_status = as.character(status)
    ),

  results %>%
    filter(phase %in% c("Phase 2.1", "Phase 2.2")) %>%
    group_by(run_id) %>%
    summarise(
      phase_group = "Phase 2",
      primary_status = if_else(
        n_distinct(phase) == 2 &&
          all(status == "PASS"),
        "PASS",
        "TIMEOUT"
      ),
      .groups = "drop"
    ),

  results %>%
    filter(phase == "Phase 3") %>%
    transmute(
      run_id,
      phase_group = "Phase 3",
      primary_status = as.character(status)
    ),

  results %>%
    filter(phase == "Phase 4") %>%
    transmute(
      run_id,
      phase_group = "Phase 4",
      primary_status = as.character(status)
    ),

  results %>%
    filter(phase == "Phase 5") %>%
    transmute(
      run_id,
      phase_group = "Phase 5",
      primary_status = as.character(status)
    )
) %>%
  left_join(
    raw_recovery_attempts,
    by = c("run_id", "phase_group")
  ) %>%
  left_join(
    valid_recovery_rows,
    by = c("run_id", "phase_group")
  ) %>%
  mutate(
    recovery_ran = !is.na(raw_recovery_phase),
    outcome = case_when(
      primary_status == "PASS" ~
        "Success (no recovery)",
      recovery_status == "PASS" ~
        "Success (with recovery)",
      recovery_ran ~
        "Failure (with recovery)",
      TRUE ~
        "Failure (no recovery)"
    ),
    final_outcome = if_else(
      outcome %in% c(
        "Success (no recovery)",
        "Success (with recovery)"
      ),
      "Success",
      "Failure"
    ),
    phase_group = factor(
      phase_group,
      levels = c(
        "Phase 1",
        "Phase 2",
        "Phase 3",
        "Phase 4",
        "Phase 5"
      )
    ),
    outcome = factor(
      outcome,
      levels = c(
        "Success (no recovery)",
        "Success (with recovery)",
        "Failure (no recovery)",
        "Failure (with recovery)"
      )
    ),
    final_outcome = factor(
      final_outcome,
      levels = c("Success", "Failure")
    )
  )
```

```{r timeout-filter-summary}
timeout_filter_summary <- removed_entries %>%
  count(
    phase,
    removal_reason,
    name = "removed_entries"
  ) %>%
  arrange(phase, removal_reason)

kable(
  timeout_filter_summary,
  caption = "Entries excluded by timeout and dependency filtering.",
  align = c("l", "l", "r")
)
```

## Theme Settings

```{r theme}
COLOR_PASS <- "#C6FFDD"
COLOR_TIMEOUT <- "#FBD786"
COLOR_FAIL <- "#f7797d"

VALUE_GRADIENT <- c(
  low = "#9796f0",
  high = "#fbc7d4"
)

SUCCESS_GRADIENT <- c(
  COLOR_FAIL,
  COLOR_TIMEOUT,
  COLOR_PASS
)

STATUS_COLORS <- c(
  "PASS" = COLOR_PASS,
  "TIMEOUT" = COLOR_TIMEOUT,
  "FAIL" = COLOR_FAIL
)

STATUS_LABELS <- c(
  "PASS" = "Pass",
  "TIMEOUT" = "Timeout",
  "FAIL" = "Fail"
)

STATUS_SHAPES <- c(
  "PASS" = 21,
  "TIMEOUT" = 24,
  "FAIL" = 22
)

FINAL_OUTCOME_COLORS <- c(
  "Success" = COLOR_PASS,
  "Failure" = COLOR_FAIL
)

DETAILED_OUTCOME_COLORS <- c(
  "Success (no recovery)" = "#C6FFDD",
  "Success (with recovery)" = "#96e6b3",
  "Failure (no recovery)" = "#FBD786",
  "Failure (with recovery)" = "#f7797d"
)

ARBITRARY_COLORS <- colorRampPalette(
  c(
    "#ff75c3",
    "#ffa647",
    "#ffe83f",
    "#9fff5b",
    "#70e2ff",
    "#cd93ff"
  )
)(10)

theme_set(
  theme_minimal(
    base_size = 11,
    base_family = "serif"
  ) +
    theme(
      text = element_text(family = "serif"),
      plot.title = element_text(
        face = "bold",
        size = 13,
        hjust = 0.5
      ),
      plot.subtitle = element_text(
        size = 9.5,
        hjust = 0.5,
        margin = margin(b = 8)
      ),
      panel.grid.minor = element_blank(),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      axis.title = element_text(face = "bold"),
      strip.text = element_text(face = "bold"),
      plot.caption = element_text(
        size = 8.5,
        hjust = 0
      ),
      plot.margin = margin(9, 9, 9, 9)
    )
)
```

# Success Rates

## Final Outcome by Main Phase

```{r final-success-rate-chart}
final_success_chart_data <- phase_outcomes %>%
  count(
    phase_group,
    final_outcome,
    name = "runs"
  ) %>%
  complete(
    phase_group,
    final_outcome = factor(
      c("Success", "Failure"),
      levels = c("Success", "Failure")
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(phase_group) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0 & share >= 0.04,
      paste0(
        percent(share, accuracy = 0.1)
      ),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  final_success_chart_data,
  aes(
    x = phase_group,
    y = share,
    fill = final_outcome
  )
) +
  geom_col(
    width = 0.7,
    color = "grey25",
    linewidth = 0.1
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    family = "serif",
    size = 3.1
  ) +
  scale_fill_manual(
    values = FINAL_OUTCOME_COLORS,
    limits = c("Success", "Failure"),
    labels = c(
      "Success" = "Successful",
      "Failure" = "Unsuccessful"
    ),
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Success Rate by Main Evaluation Phase",
    x = "Evaluation phase",
    y = "Share of runs",
    fill = "Outcome"
  )
```

## Direct, Recovered, and Failed Outcomes

```{r detailed-outcome-chart}
detailed_outcome_chart_data <- phase_outcomes %>%
  count(
    phase_group,
    outcome,
    name = "runs"
  ) %>%
  complete(
    phase_group,
    outcome = factor(
      c(
        "Success (no recovery)",
        "Success (with recovery)",
        "Failure (no recovery)",
        "Failure (with recovery)"
      ),
      levels = c(
        "Success (no recovery)",
        "Success (with recovery)",
        "Failure (no recovery)",
        "Failure (with recovery)"
      )
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(phase_group) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0 & share >= 0.04,
      percent(share, accuracy = 0.1),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  detailed_outcome_chart_data,
  aes(
    x = phase_group,
    y = share,
    fill = outcome
  )
) +
  geom_col(
    width = 0.7,
    color = "grey25",
    linewidth = 0.25
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    family = "serif",
    size = 3
  ) +
  scale_fill_manual(
    values = DETAILED_OUTCOME_COLORS,
    limits = c(
      "Success (no recovery)",
      "Success (with recovery)",
      "Failure (no recovery)",
      "Failure (with recovery)"
    ),
    labels = c(
      "Success (no recovery)" =
        "Success",
      "Success (with recovery)" =
        "Success after recovery",
      "Failure (no recovery)" =
        "Failure (no recovery)",
      "Failure (with recovery)" =
        "Recovery failed"
    ),
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Detailed Success and Failure Rate by Evaluation Phase",
    x = "Evaluation phase",
    y = "Share of runs",
    fill = "Outcome category"
  )
```

```{r success-rate-table}
success_rate_table <- phase_outcomes %>%
  count(
    phase_group,
    outcome,
    name = "runs"
  ) %>%
  complete(
    phase_group,
    outcome,
    fill = list(runs = 0)
  ) %>%
  pivot_wider(
    names_from = outcome,
    values_from = runs
  ) %>%
  arrange(phase_group)

kable(
  success_rate_table,
  caption = "Run counts by phase outcome.",
  align = c("l", "r", "r", "r", "r")
)
```

# Final Success Rate by Input Variables

## Phase 1: Initial Network Formation

```{r phase1-input-chart}
phase1_input_data <- results %>%
  filter(phase == "Phase 1") %>%
  select(
    run_id,
    initial_nodes,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 1") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase1_input_plot <- ggplot(
  phase1_input_data,
  aes(
    x = initial_nodes,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(8, 18),
    breaks = pretty_breaks(n = 3)
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = paste(
      "Phase 1 Initial-Network Formation:",
      "Final Success Rate by Network Size and Neighbor Limit"
    ),
    subtitle = paste(
      "Bubble fill and label show final success rate including successful R1 recovery;",
      "bubble size shows the number of runs."
    ),
    x = "Initial node count",
    y = "Maximum neighbors per node",
    fill = "Final success rate",
    size = "Number of runs"
  )

phase1_input_plot
```

## Phase 3: Single-Node Failure Repair

```{r phase3-input-chart}
phase3_input_data <- results %>%
  filter(phase == "Phase 3") %>%
  select(
    run_id,
    initial_nodes,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 3") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    initial_nodes,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase3_input_plot <- ggplot(
  phase3_input_data,
  aes(
    x = initial_nodes,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(8, 18),
    breaks = pretty_breaks(n = 3)
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = paste(
      "Phase 3 Single-Node Failure Repair:",
      "Final Success Rate by Network Size and Neighbor Limit"
    ),
    subtitle = paste(
      "Bubble fill and label show final success rate including successful R3 recovery;",
      "bubble size shows the number of runs."
    ),
    x = "Initial node count",
    y = "Maximum neighbors per node",
    fill = "Final success rate",
    size = "Number of runs"
  )

phase3_input_plot
```

## Phase 4: Adding Nodes

```{r phase4-input-chart}
phase4_input_data <- results %>%
  filter(phase == "Phase 4") %>%
  select(
    run_id,
    added_node_count,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 4") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    added_node_count,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase4_input_plot <- ggplot(
  phase4_input_data,
  aes(
    x = added_node_count,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(8, 18),
    breaks = pretty_breaks(n = 3)
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = paste(
      "Phase 4 Node Addition:",
      "Final Success Rate by Added Nodes and Neighbor Limit"
    ),
    subtitle = paste(
      "Bubble fill and label show final success rate including successful R4 recovery;",
      "bubble size shows the number of runs."
    ),
    x = "Number of added nodes",
    y = "Maximum neighbors per node",
    fill = "Final success rate",
    size = "Number of runs"
  )

phase4_input_plot
```

## Phase 5: Removing Multiple Nodes

```{r phase5-input-chart}
phase5_input_data <- results %>%
  filter(phase == "Phase 5") %>%
  select(
    run_id,
    removed_node_count,
    max_neighbors
  ) %>%
  left_join(
    phase_outcomes %>%
      filter(phase_group == "Phase 5") %>%
      select(run_id, final_outcome),
    by = "run_id"
  ) %>%
  group_by(
    removed_node_count,
    max_neighbors
  ) %>%
  summarise(
    runs = n(),
    success_rate = mean(
      final_outcome == "Success",
      na.rm = TRUE
    ),
    .groups = "drop"
  )

phase5_input_plot <- ggplot(
  phase5_input_data,
  aes(
    x = removed_node_count,
    y = max_neighbors
  )
) +
  geom_point(
    aes(
      size = runs,
      fill = success_rate
    ),
    shape = 21,
    color = "grey20",
    stroke = 0.5
  ) +
  geom_text(
    aes(
      label = percent(
        success_rate,
        accuracy = 1
      )
    ),
    family = "serif",
    size = 3
  ) +
  scale_fill_gradientn(
    colours = SUCCESS_GRADIENT,
    values = c(0, 0.5, 1),
    limits = c(0, 1),
    labels = percent_format()
  ) +
  scale_size_continuous(
    range = c(8, 18),
    breaks = pretty_breaks(n = 3)
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = paste(
      "Phase 5 Multiple-Node Failure Repair:",
      "Final Success Rate by Removed Nodes and Neighbor Limit"
    ),
    subtitle = paste(
      "Bubble fill and label show final success rate including successful R5 recovery;",
      "bubble size shows the number of runs."
    ),
    x = "Number of removed nodes",
    y = "Maximum neighbors per node",
    fill = "Final success rate",
    size = "Number of runs"
  )

phase5_input_plot
```

## Combined Input-Variable Comparison

```{r combined-input-chart, fig.width=10, fig.height=8.8}
(
  phase1_input_plot +
    phase3_input_plot +
    phase4_input_plot +
    phase5_input_plot
) +
  plot_layout(
    ncol = 2,
    guides = "collect"
  ) +
  plot_annotation(
    title = paste(
      "Final Success Rates Across Tested Network Sizes,",
      "Neighbor Limits, Node Additions, and Node Removals"
    ),
    subtitle = paste(
      "Final success includes successful replacement-based recovery;",
      "bubble size represents the number of repeated runs."
    ),
    theme = theme(
      plot.title = element_text(
        family = "serif",
        face = "bold",
        size = 14,
        hjust = 0.5
      ),
      plot.subtitle = element_text(
        family = "serif",
        size = 10,
        hjust = 0.5
      )
    )
  ) &
  theme(
    text = element_text(family = "serif"),
    legend.position = "bottom"
  )
```

# Stability Checks

```{r stability-success-chart}
stability_labels <- c(
  "S1" = "After initial formation (S1)",
  "S3" = "After single-failure repair (S3)",
  "S4" = "After adding nodes (S4)",
  "S5" = "After multiple failures (S5)",
  "SR" = "After replacement recovery (SR)"
)

stability_chart_data <- results %>%
  filter(phase %in% STABILITY_PHASES) %>%
  mutate(
    phase = factor(
      phase,
      levels = STABILITY_PHASES
    ),
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  ) %>%
  count(
    phase,
    status,
    name = "runs"
  ) %>%
  complete(
    phase = factor(
      STABILITY_PHASES,
      levels = STABILITY_PHASES
    ),
    status = factor(
      STATUS_LEVELS,
      levels = STATUS_LEVELS
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(phase) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0,
      paste0(
        percent(share, accuracy = 0.1),
        "\n(n = ", runs, ")"
      ),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  stability_chart_data,
  aes(
    x = phase,
    y = share,
    fill = status
  )
) +
  geom_col(
    width = 0.65,
    color = "grey25",
    linewidth = 0.25
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    family = "serif",
    size = 3
  ) +
  coord_flip() +
  scale_x_discrete(
    labels = stability_labels,
    limits = rev(STABILITY_PHASES)
  ) +
  scale_fill_manual(
    values = STATUS_COLORS,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Outcomes of the 10-Second Post-Phase Stability Checks",
    subtitle = paste(
      "Each bar shows whether the topology remained valid for the full",
      "10-second observation window after the named operation."
    ),
    x = "Stability check and preceding operation",
    y = "Share of stability checks",
    fill = "Recorded status"
  )
```

# Failure Detection Time

```{r phase2-time-chart}
phase2_time_data <- results %>%
  filter(
    phase %in% c("Phase 2.1", "Phase 2.2")
  ) %>%
  mutate(
    detection_milestone = factor(
      phase,
      levels = c(
        "Phase 2.1",
        "Phase 2.2"
      ),
      labels = c(
        "First failure report\n(Phase 2.1)",
        "All expected failure reports\n(Phase 2.2)"
      )
    ),
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase2_time_data,
  aes(
    x = detection_milestone,
    y = elapsed_seconds
  )
) +
  geom_boxplot(
    aes(fill = detection_milestone),
    width = 0.55,
    outlier.shape = NA,
    alpha = 0.65
  ) +
  geom_jitter(
    aes(color = status),
    width = 0.12,
    height = 0,
    size = 2.1,
    alpha = 0.8
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_manual(
    values = ARBITRARY_COLORS[c(2, 9)],
    limits = levels(
      phase2_time_data$detection_milestone
    ),
    drop = FALSE,
    guide = "none"
  ) +
  scale_color_manual(
    values = STATUS_COLORS,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  labs(
    title = "Failure-Detection Time: First Report Compared with Complete Expected Reporting",
    subtitle = paste(
      "Phase 2.1 ends at the first failure report; Phase 2.2 ends when all expected",
      "neighbors have reported. Dashed line: configured 120-second timeout."
    ),
    x = "Failure-detection milestone",
    y = "Elapsed time after node termination (seconds)",
    color = "Recorded status"
  )
```

# Main-Phase Completion Time and Input Effects

## Phase 1: Initial Network Formation

```{r phase1-time-impact-chart}
phase1_time_data <- results %>%
  filter(phase == "Phase 1") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase1_time_data,
  aes(
    x = initial_nodes,
    y = elapsed_seconds
  )
) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.13,
      height = 0
    ),
    size = 3.4,
    color = "grey15",
    stroke = 0.5,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = "Initial Network Formation Time by Initial Node Count and Neighbor Limit",
    subtitle = paste(
      "Point fill represents the maximum neighbors allowed per node;",
      "point shape represents status. Dashed line: configured 120-second timeout."
    ),
    x = "Initial node count",
    y = "Time to form a valid full-neighbor topology (seconds)",
    fill = "Maximum neighbors per node",
    shape = "Recorded status"
  )
```

## Phase 3: Repair After One Node Failure

```{r phase3-time-impact-chart}
phase3_time_data <- results %>%
  filter(phase == "Phase 3") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase3_time_data,
  aes(
    x = initial_nodes,
    y = elapsed_seconds
  )
) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.13,
      height = 0
    ),
    size = 3.4,
    color = "grey15",
    stroke = 0.5,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 180,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = "Single-Node Failure Repair Time by Initial Node Count and Neighbor Limit",
    subtitle = paste(
      "Point fill represents the maximum neighbors allowed per node;",
      "point shape represents status. Dashed line: configured 180-second timeout."
    ),
    x = "Initial node count",
    y = "Time to restore a valid full-neighbor topology (seconds)",
    fill = "Maximum neighbors per node",
    shape = "Recorded status"
  )
```

## Phase 4: Adding Nodes

```{r phase4-time-impact-chart}
phase4_time_data <- results %>%
  filter(phase == "Phase 4") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase4_time_data,
  aes(
    x = added_node_count,
    y = elapsed_seconds
  )
) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.13,
      height = 0
    ),
    size = 3.4,
    color = "grey15",
    stroke = 0.5,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = "Node-Addition Convergence Time by Added Node Count and Neighbor Limit",
    subtitle = paste(
      "Point fill represents the maximum neighbors allowed per node;",
      "point shape represents status. Dashed line: configured 120-second timeout."
    ),
    x = "Number of added nodes",
    y = "Time until all active nodes have valid full neighbor sets (seconds)",
    fill = "Maximum neighbors per node",
    shape = "Recorded status"
  )
```

## Phase 5: Repair After Multiple Node Failures

```{r phase5-time-impact-chart}
phase5_time_data <- results %>%
  filter(phase == "Phase 5") %>%
  mutate(
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  )

ggplot(
  phase5_time_data,
  aes(
    x = removed_node_count,
    y = elapsed_seconds
  )
) +
  geom_point(
    aes(
      fill = max_neighbors,
      shape = status
    ),
    position = position_jitter(
      width = 0.13,
      height = 0
    ),
    size = 3.4,
    color = "grey15",
    stroke = 0.5,
    alpha = 0.85
  ) +
  geom_hline(
    yintercept = 180,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_fill_gradient(
    low = VALUE_GRADIENT["low"],
    high = VALUE_GRADIENT["high"]
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = "Multiple-Node Failure Repair Time by Removed Node Count and Neighbor Limit",
    subtitle = paste(
      "Point fill represents the maximum neighbors allowed per node;",
      "point shape represents status. Dashed line: configured 180-second timeout."
    ),
    x = "Number of removed nodes",
    y = "Time to restore a valid full-neighbor topology (seconds)",
    fill = "Maximum neighbors per node",
    shape = "Recorded status"
  )
```

# Replacement-Based Recovery Completion Time

```{r recovery-time-impact-chart}
recovery_trigger_data <- results %>%
  filter(
    phase %in% c(
      "Phase 1",
      "Phase 3",
      "Phase 4",
      "Phase 5"
    )
  ) %>%
  transmute(
    run_id,
    trigger_phase = phase,
    trigger_problem_count = problem_count,
    trigger_max_neighbors = max_neighbors
  )

recovery_time_data <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  transmute(
    run_id,
    recovery_phase = factor(
      phase,
      levels = RECOVERY_PHASES
    ),
    recovery_status = factor(
      status,
      levels = STATUS_LEVELS
    ),
    elapsed_seconds,
    trigger_phase = recode(
      phase,
      "R1" = "Phase 1",
      "R3" = "Phase 3",
      "R4" = "Phase 4",
      "R5" = "Phase 5"
    )
  ) %>%
  left_join(
    recovery_trigger_data,
    by = c("run_id", "trigger_phase")
  )

recovery_phase_colors <- setNames(
  ARBITRARY_COLORS[c(1, 4, 7, 10)],
  RECOVERY_PHASES
)

recovery_phase_labels <- c(
  "R1" = "R1: after initial formation",
  "R3" = "R3: after single-node failure repair",
  "R4" = "R4: after adding nodes",
  "R5" = "R5: after multiple-node failure repair"
)

ggplot(
  recovery_time_data,
  aes(
    x = trigger_problem_count,
    y = elapsed_seconds
  )
) +
  geom_point(
    aes(
      color = recovery_phase,
      shape = recovery_status,
      size = trigger_max_neighbors
    ),
    position = position_jitter(
      width = 0.12,
      height = 0
    ),
    alpha = 0.82
  ) +
  geom_hline(
    yintercept = 120,
    linetype = "dashed",
    linewidth = 0.5,
    color = "grey30"
  ) +
  scale_color_manual(
    values = recovery_phase_colors,
    limits = RECOVERY_PHASES,
    labels = recovery_phase_labels,
    drop = FALSE
  ) +
  scale_shape_manual(
    values = STATUS_SHAPES,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_size_continuous(
    range = c(2.5, 5.5),
    breaks = pretty_breaks(n = 4)
  ) +
  scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  labs(
    title = "Replacement-Based Recovery Time by Triggering Operation and Initial Problem Count",
    subtitle = paste(
      "R1, R3, R4, and R5 restart deficient/problematic nodes and wait for a valid topology.",
      "Dashed line: configured 120-second recovery timeout."
    ),
    x = "Deficient or problematic nodes that triggered recovery",
    y = "Replacement-based recovery time (seconds)",
    color = "Recovery trigger",
    shape = "Recorded status",
    size = "Maximum neighbors per node"
  )
```

# Problematic Nodes in Failed Main Phases

## Phase 1: Initial Network Formation

```{r phase1-problem-count-chart}
phase1_problem_data <- results %>%
  filter(
    phase == "Phase 1",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase1_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 1 initial-network formation",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Deficient Nodes in Failed Phase 1 Initial-Network Formation Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase1_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Deficient Nodes Present When Initial Network Formation Failed",
      subtitle = "Each bar counts failed Phase 1 runs with the displayed number of deficient nodes.",
      x = "Deficient nodes at the end of Phase 1",
      y = "Number of failed runs"
    )
}
```

## Phase 3: Repair After One Node Failure

```{r phase3-problem-count-chart}
phase3_problem_data <- results %>%
  filter(
    phase == "Phase 3",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase3_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 3 single-node repair",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Deficient Nodes in Failed Single-Node Failure Repair Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase3_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Deficient Nodes Remaining When Single-Node Failure Repair Failed",
      subtitle = "Each bar counts failed Phase 3 runs with the displayed number of deficient nodes.",
      x = "Deficient nodes at the end of Phase 3",
      y = "Number of failed runs"
    )
}
```

## Phase 4: Adding Nodes

```{r phase4-problem-count-chart}
phase4_problem_data <- results %>%
  filter(
    phase == "Phase 4",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase4_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 4 node-addition",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Problematic Nodes in Failed Node-Addition Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase4_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Problematic Nodes Remaining When Node Addition Failed",
      subtitle = "Each bar counts failed Phase 4 runs with the displayed number of problematic nodes.",
      x = "Problematic nodes at the end of Phase 4",
      y = "Number of failed runs"
    )
}
```

## Phase 5: Repair After Multiple Node Failures

```{r phase5-problem-count-chart}
phase5_problem_data <- results %>%
  filter(
    phase == "Phase 5",
    status != "PASS"
  ) %>%
  count(
    problem_count,
    name = "runs"
  )

if (nrow(phase5_problem_data) == 0) {
  ggplot() +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = paste(
        "No failed Phase 5 multiple-node repair",
        "records remained after timeout filtering."
      ),
      family = "serif",
      size = 4
    ) +
    xlim(-1, 1) +
    ylim(-1, 1) +
    labs(
      title = "Problematic Nodes in Failed Multiple-Node Failure Repair Runs",
      x = NULL,
      y = NULL
    ) +
    theme_void(base_family = "serif")
} else {
  ggplot(
    phase5_problem_data,
    aes(
      x = problem_count,
      y = runs,
      fill = problem_count
    )
  ) +
    geom_col(
      width = 0.75,
      color = "grey25",
      linewidth = 0.25
    ) +
    geom_text(
      aes(label = runs),
      vjust = -0.3,
      family = "serif",
      size = 3.2
    ) +
    scale_fill_gradient(
      low = VALUE_GRADIENT["low"],
      high = VALUE_GRADIENT["high"],
      guide = "none"
    ) +
    scale_x_continuous(
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks(),
      expand = expansion(
        mult = c(0, 0.12)
      )
    ) +
    labs(
      title = "Problematic Nodes Remaining When Multiple-Node Failure Repair Failed",
      subtitle = "Each bar counts failed Phase 5 runs with the displayed number of problematic nodes.",
      x = "Problematic nodes at the end of Phase 5",
      y = "Number of failed runs"
    )
}
```

# Replacement-Based Recovery Success Rates

```{r recovery-success-chart}
recovery_labels <- c(
  "R1" = "After initial formation (R1)",
  "R3" = "After single-node failure repair (R3)",
  "R4" = "After adding nodes (R4)",
  "R5" = "After multiple-node failure repair (R5)"
)

recovery_success_data <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  mutate(
    phase = factor(
      phase,
      levels = RECOVERY_PHASES
    ),
    status = factor(
      status,
      levels = STATUS_LEVELS
    )
  ) %>%
  count(
    phase,
    status,
    name = "runs"
  ) %>%
  complete(
    phase = factor(
      RECOVERY_PHASES,
      levels = RECOVERY_PHASES
    ),
    status = factor(
      STATUS_LEVELS,
      levels = STATUS_LEVELS
    ),
    fill = list(runs = 0)
  ) %>%
  group_by(phase) %>%
  mutate(
    total_runs = sum(runs),
    share = if_else(
      total_runs > 0,
      runs / total_runs,
      0
    ),
    label = if_else(
      runs > 0,
      paste0(
        percent(share, accuracy = 0.1),
        "\n(n = ", runs, ")"
      ),
      ""
    )
  ) %>%
  ungroup()

ggplot(
  recovery_success_data,
  aes(
    x = phase,
    y = share,
    fill = status
  )
) +
  geom_col(
    width = 0.65,
    color = "grey25",
    linewidth = 0.25
  ) +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    family = "serif",
    size = 3
  ) +
  coord_flip() +
  scale_x_discrete(
    labels = recovery_labels,
    limits = rev(RECOVERY_PHASES)
  ) +
  scale_fill_manual(
    values = STATUS_COLORS,
    limits = STATUS_LEVELS,
    labels = STATUS_LABELS,
    drop = FALSE
  ) +
  scale_y_continuous(
    labels = percent_format(),
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title = "Outcome of Replacement-Based Recovery Attempts by Triggering Operation",
    subtitle = paste(
      "Each recovery phase restarts deficient/problematic processes and waits",
      "up to 120 seconds for a valid full-neighbor topology."
    ),
    x = "Operation that triggered replacement-based recovery",
    y = "Share of valid recovery attempts",
    fill = "Recorded status"
  )
```

```{r recovery-success-table}
recovery_success_summary <- results %>%
  filter(phase %in% RECOVERY_PHASES) %>%
  group_by(phase) %>%
  summarise(
    attempts = n(),
    passes = sum(status == "PASS"),
    timeouts = sum(status == "TIMEOUT"),
    failures = sum(status == "FAIL"),
    success_rate = mean(status == "PASS"),
    .groups = "drop"
  ) %>%
  mutate(
    phase = factor(
      phase,
      levels = RECOVERY_PHASES
    )
  ) %>%
  arrange(phase)

kable(
  recovery_success_summary,
  caption = "Valid replacement-based recovery attempts after timeout filtering.",
  digits = 3,
  align = c("l", "r", "r", "r", "r", "r")
)
```
